\documentclass[pdflatex,sn-mathphys-num]{sn-jnl}

\usepackage{enumitem}
\usepackage{graphicx}%
\usepackage{multirow}%
\usepackage{amsmath,amssymb,amsfonts}%
\usepackage{amsthm}%
\usepackage{mathrsfs}%
\usepackage[title]{appendix}%
\usepackage{xcolor}%
\usepackage{textcomp}%
\usepackage{manyfoot}%
\usepackage{booktabs}%
\usepackage{algorithm}%
\usepackage{algorithmicx}%
\usepackage{algpseudocode}%
\usepackage{listings}
\usepackage{aliascnt}
\usepackage{slashed}

\renewcommand{\sectionautorefname}{Section}

%% as per the requirement new theorem styles can be included as shown below
\theoremstyle{thmstyleone}
\newtheorem{theorem}{Theorem}

% Lemma
\newaliascnt{lemma}{theorem}
\newtheorem{lemma}[lemma]{Lemma}
\aliascntresetthe{lemma}
\providecommand*{\lemmaautorefname}{Lemma}

% Axiom
\newaliascnt{axiom}{theorem}
\newtheorem{axiom}[axiom]{Axiom}
\aliascntresetthe{axiom}
\providecommand*{\axiomautorefname}{Axiom}

% Corollary
\newaliascnt{corollary}{theorem}
\newtheorem{corollary}[corollary]{Corollary}
\aliascntresetthe{corollary}
\providecommand*{\corollaryautorefname}{Corollary}

% Proposition
\newaliascnt{proposition}{theorem}
\newtheorem{proposition}[proposition]{Proposition}
\aliascntresetthe{proposition}
\providecommand*{\propositionautorefname}{Proposition}

\theoremstyle{thmstyletwo}%
\newtheorem{example}{Example}%
\newtheorem{remark}{Remark}%

\theoremstyle{thmstylethree}%
\newtheorem{definition}{Definition}%

\raggedbottom
%%\unnumbered% uncomment this for unnumbered level heads

% custom commands
\newcommand{\SU}[1]{\mathrm{SU(#1)}}
\newcommand{\SMSubgroup}{\SU{3}\times\SU{2}\times\U{1}}
\newcommand{\SO}[1]{\mathrm{SO(#1)}}
\newcommand{\U}[1]{\mathrm{U(#1)}}
\newcommand{\E}[1]{\mathrm{E_{#1}}}
\newcommand{\M}{\mathcal{M}}
\newcommand{\Oct}{\mathbb{O}}
\newcommand{\jalg}{J_3(\mathbb{O})}
\newcommand{\SOTen}{\SO{10}}
\newcommand{\UOne}{\U{1}}
\newcommand{\ESix}{\E{6}}
\newcommand{\SOTenXUOne}{\SOTen \times \UOne}
\newcommand{\MCoset}{\frac{\ESix}{\SOTenXUOne}}
\newcommand{\MCosetInline}{\ESix/(\SOTenXUOne)}
\newcommand{\ESixBreaking}{\ESix \;\to\; \SOTenXUOne}
\newcommand{\map}[3]{#1 \ : \ \#2 \;\to\; \#3}
\newcommand{\set}[2]{\{ #1 \,:\, #2 \}}
\newcommand{\Herm}[2]{\mathrm{Herm}_{#1}(#2)}
\newcommand{\chr}[1]{\mathrm{char}(#1)}
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\Tr}{\operatorname{Tr}}
\newcommand{\s}{\hspace{.1em}}
\newcommand{\sm}{\hspace{.065em}}
\newcommand{\Str}{\operatorname{Str}}
\newcommand{\Spin}{\operatorname{Spin}}
\newcommand{\appref}[1]{\hyperref[#1]{Appendix~\ref*{#1}}}
\newcommand{\subsecref}[1]{\hyperref[#1]{Section~\ref*{#1}}}
\newcommand{\smexp}[1]{^{\sm #1}}
\newcommand{\Hess}[1]{\operatorname{Hess}}
\newcommand{\dv}[1]{\mathrm{d}\smexp{#1}}

\renewcommand{\arraystretch}{1.25}

\begin{document}

\title[Universal Coset Field Theory]{Universal Coset Field Theory: An Albert--EIII Swampland Criterion for Heterotic Vacua}

\author*[1]{\fnm{Brandon} \sur{Belna}}\email{bbelna@aol.com, brandon@belna.org, bbelna@iu.edu}
\affil*[1]{\orgdiv{Department of Mathematics}, \orgname{Indiana University East}, \orgaddress{\street{2325 Chester Blvd}, \city{Richmond}, \postcode{47374}, \state{IN}, \country{USA}}}

\abstract{%
We develop Universal Coset Field Theory (UCFT), a four-dimensional quantum
field theory built from a single quantum-mechanical datum---the state space of
the exceptional Jordan (Albert) algebra $\jalg$, with reduced structure group
$\ESix$---and use it to formulate a new, sharp swampland criterion for
heterotic string vacua. An $\ESix$-invariant coercive potential attains its
minimum precisely on Cartan's Hermitian symmetric space EIII,
$\MCosetInline$, whose $32$ real tangent directions form a single
\emph{irreducible} $\SOTenXUOne$ multiplet with complexification
$\mathbf{16}_{-3}\oplus\overline{\mathbf{16}}_{+3}$ and carry a unique,
positive-definite invariant metric. A spacetime-filling configuration of these
Goldstone fields immerses a four-manifold into EIII with nondegenerate
Riemannian first fundamental form; Lorentzian spacetime follows by
Osterwalder--Schrader reconstruction, and one-loop fluctuations induce an
Einstein--Hilbert term in the sense of Sakharov, with no fundamental graviton.
We then show that this coset sector is the gauge-unfixed Higgs orbit of an
$E_8\times E_8$ heterotic $\ESix$ compactification: the visible two-derivative
bosonic action and $\SOTenXUOne_\psi$ current algebra match those of UCFT, a
gravity-from-field-theory correspondence realized concretely by a
$\mathbb Z_{12}$ asymmetric orbifold with three generations and an adjoint
Higgs. Our main result is the \emph{Albert--EIII swampland theorem}: within the
Albert-selected heterotic class, a four-dimensional effective theory lies in
the landscape only if its gauge-unfixed Higgs/moduli sector is the EIII coset
with the stated tangent representation, invariant metric, gauge data, anomaly
and Green--Schwarz matching, and worldsheet consistency; every other
Albert-selected effective theory lies in the Albert--EIII swampland, admitting
no heterotic UV completion realizing the UCFT correspondence. This is a
relative, class-restricted statement, not a universal one, and it makes the
$\mathbb Z_{12}$ model an explicit leading landscape candidate. A functional
renormalization-group analysis exhibits a unique asymptotically safe fixed
point with grand-unified scale
$M_{\mathrm{GUT}}\simeq2\times10\smexp{16}\,\mathrm{GeV}$. We separate what is
fixed by representation theory from what requires further dynamical input, and
delineate the open problems.}

\keywords{swampland, exceptional Jordan algebra, $E_6$, heterotic string,
$\mathbb Z_{12}$ orbifold, coset field theory, EIII, induced gravity, emergent
spacetime, asymptotic safety, grand unification}

%%\pacs[JEL Classification]{D8, H51}

%%\pacs[MSC Classification]{35A01, 65L10, 65L12, 65L20, 65L70}

\maketitle

%======================================================================%
\section{Introduction}
%======================================================================%

Exceptional algebraic structures recur throughout high-energy physics. The
exceptional Jordan (Albert) algebra $\jalg$ of $3\times3$ Hermitian octonionic
matrices has automorphism group $F_{4}$ and reduced structure group
$\ESix=\Str_{0}(\jalg)$, the invariance group of its cubic norm
\cite{Jacobson:1968,Springer:2000,McCrimmon:2004}. In turn $\ESix$ contains
$\SOTenXUOne$, under which the fundamental $\mathbf{27}$ branches as
\[
  \mathbf{27}=\mathbf{16}_{+1}\oplus\mathbf{10}_{-2}\oplus\mathbf{1}_{+4},
\]
the $\mathbf{16}$ of $\Spin(10)$ carrying one Standard-Model family together
with a right-handed neutrino \cite{Slansky:1981}. Formally real Jordan algebras
were introduced precisely as the algebra of observables of a quantum system;
$\jalg$ is the unique exceptional member of their classification. This gives a
sharp conceptual starting point: take a quantum state space as the only datum
and ask how much of four-dimensional physics its internal symmetry fixes.

The construction rests on two axioms, stated in
\subsecref{subsec:Axioms}. The first posits a maximally symmetric initial state
in $\jalg$; the second posits the usual quantum-mechanical kinematics of a
universal wavefunction with unitary evolution. From these we build a field
theory, not by adding structure, but by following the consequences of
symmetry breaking on the Jordan state space. An $\ESix$-invariant polynomial
potential, built from the quadratic and cubic invariants $Q$ and $N$, is
coercive and is minimized exactly on the orbit
\[
  \ESix\cdot X_{0}\cong\MCoset,
\]
the compact Hermitian symmetric space EIII \cite{Helgason:1978}, of real
dimension $78-46=32$. The $32$ Goldstone directions form a single irreducible
multiplet of $H=\SOTenXUOne$, whose complexification is
$\mathbf{16}_{-3}\oplus\overline{\mathbf{16}}_{+3}$; the invariant metric is
therefore unique up to scale and, since $H$ is compact, positive definite.

The central claim of the paper is that spacetime and gravity are not postulated
but emerge from this coset sector. A spacetime-filling configuration of the
Goldstone fields immerses a four-manifold into EIII; its first fundamental form
is a genuine, nondegenerate Riemannian metric, so the four-dimensional geometry
is induced by the field configuration rather than fixed by hand. Because the
functional integral is defined in Euclidean signature---as required for the
Osterwalder--Schrader reconstruction invoked in
\autoref{ax:AxiomII}---physical Lorentzian spacetime is recovered by
continuation. Quantizing the $32$ scalars, the gauge fields, and a chiral
$\mathbf{16}$, one-loop fluctuations then induce an Einstein--Hilbert term in
the sense of Sakharov \cite{SakharovInducedGravity,AdlerInducedGravity}; the metric propagates only through
this induced action, and there is no fundamental graviton.

Two further results complete the picture. First, a functional
renormalization-group analysis of the coset-field action exhibits a unique
ultraviolet-attractive non-Gaussian fixed point at which all higher-curvature
and higher-scalar operators are irrelevant; within the truncation the theory is
asymptotically safe, and downward running of the gauge couplings fixes a
grand-unified scale $M_{\mathrm{GUT}}\simeq2\times10\smexp{16}\,\mathrm{GeV}$.
Second, the $\ESix$ branchings supply the grand-unified matter skeleton and its
anomaly conditions. We are careful to separate theorem from construction from
conjecture. What is proved: the coercive potential and its EIII minimum, the
irreducibility and unique positive metric of the $32$-scalar sector, the
emergent Riemannian geometry, the induced Einstein--Hilbert term, and the
fixed-point structure of the truncated flow. What is supplied by additional
dynamical input, and left open: the complete low-energy spectrum, family
replication, the cosmological constant, and a full ultraviolet completion.

The paper is organized as follows. \autoref{sec:AxiomsAlbertSSB} states the
axioms, recalls the Albert algebra and its $\ESix$ symmetry, and constructs the
symmetry-breaking potential and its vacuum manifold.
\autoref{sec:EmergentFields} derives the emergent four-dimensional geometry and
the low-energy field content. \autoref{sec:sigma} defines the coset
$\sigma$-model, quantizes it, and derives the induced Einstein--Hilbert term and
the coset mass spectrum. \autoref{sec:FRG} presents the renormalization-group
flow, the non-Gaussian fixed point, and the grand-unified matching scale.
Proofs and technical computations are collected in the appendices.

%======================================================================%
\section{Axioms, the Albert Algebra, and Spontaneous Symmetry Breaking}
\label{sec:AxiomsAlbertSSB}
%======================================================================%
In this section, we introduce our two fundamental axioms, recall the definition and key properties of the Albert algebra $J_{3}(\mathbb O)$ and its $\ESix$ symmetry (with proofs in \appref{app:Albert}), exhibit a purely algebraic polynomial potential whose minima break $\ESix\to \SOTenXUOne$, and count the resulting $32$ Goldstone directions.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Axioms}\label{subsec:Axioms}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{axiom}[Maximally symmetric vacuum]\label{ax:AxiomI}
The universe begins in a unique state $\Phi\in\jalg$ that is fixed by every element of its structure group.
\end{axiom}
\begin{axiom}[Universal wavefunction]\label{ax:AxiomII}
Physical states $\psi\in\mathcal H$ evolve through a one-parameter family
$\{U(t)\}_{t\in\mathbb R}$ of unitary operators satisfying $U(0)=\mathrm{Id}$, $U(t+s)=U(t)U(s)$, and strong continuity.
\end{axiom}

\begin{remark}
\autoref{ax:AxiomII} provides the kinematical Hilbert space and the one-parameter
family of unitary operators.  Whenever we later write a functional integral, we treat it as a formal generator of connected Green functions; its constructive definition follows from the Osterwalder-Schrader reconstruction theorem applied to the Euclidean correlation functions \cite{GlimmJaffe:1987}.
\end{remark}


No additional axioms are introduced; all further constructions follow as definitions or theorems derived from these two axioms.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{The Albert Algebra}
\label{subsec:Albert}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Proofs for this subsection are provided in \appref{app:Albert}.

\begin{definition}[Jordan algebra {\cite{Jacobson:1968}}]
Let $F$ be a field with $\operatorname{char} F \neq 2$.  
A \emph{Jordan algebra} is a commutative algebra $(A,\circ)$ satisfying
\[
  a\circ(b\circ a\smexp{2}) \;=\;(a\circ b)\circ a\smexp{2},
  \quad a,b\in A.
\]
\end{definition}

\begin{definition}[Albert algebra {\cite{Albert:1934,McCrimmon:2004}}]
The \emph{Albert algebra} is
\[
  \jalg=\{X\in M_{3}(\Oct) : X=X\smexp{\dagger}\},
  \quad
  X\circ Y=\frac12\,(XY+YX).
\]
\end{definition}

\begin{theorem}\label{thm:JordanDim}
The Albert algebra is a $27$-dimensional real Jordan algebra.
\end{theorem}

\begin{theorem}[Quadratic and cubic invariants]\label{thm:Invs}
$\jalg$ admits  
\[
  Q(X)=\Tr(X\smexp{2}), 
  \quad
  N(X)=\det_{\Oct}(X),
\]
both preserved by its structure group.
\end{theorem}

\begin{theorem}[Structure group {\cite{Springer:2000}}]\label{thm:E6}
The structure group of $\jalg$ is the simply connected exceptional Lie group $\ESix$.
\end{theorem}

\begin{theorem}[Orbit classification]\label{thm:OrbitClass}
For $X,Y\in\jalg$,
\[
  \bigl(Q(X),N(X)\bigr)=\bigl(Q(Y),N(Y)\bigr)
\]
if and only if there exists $g\in\ESix$ such that $g\cdot X = Y$.
\end{theorem}

\begin{corollary}[Existence of an $\SOTenXUOne$ stabiliser]
\label{cor:Isotropy}
There exists $X_{0}\in J_{3}(\mathbb{O})$ with
$\mathrm{Stab}_{\ESix}(X_{0})\cong \SOTen\times \UOne$.
\end{corollary}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Polynomial Symmetry-Breaking Potential}\label{subsec:PolyPot}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Set
\[
  I_{2}(X)=Q(X),
  \quad
  I_{3}(X)=N(X),
  \quad
  c_{2}=I_{2}(X_{0}),
  \quad
  c_{3}=I_{3}(X_{0}).
\]
In particular, each simultaneous level set $\{I_{2}=c_{2},\,I_{3}=c_{3}\}$ is exactly one $\ESix$-orbit, so by choosing $c_{2}=I_{2}(X_{0})$ and $c_{3}=I_{3}(X_{0})$, we identify the zero locus of $P(X)$ with $\ESix \cdot X_{0}$. In addition, define
\begin{equation}\label{eq:Pdef}
\begin{aligned}
  P(X)
  &=\bigl[I_{2}(X)-c_{2}\bigr]\smexp{2}
  +\bigl[I_{3}(X)-c_{3}\bigr]\smexp{2},\\[2pt]
  V(X)
  &=P(X)
  +\alpha\,[I_{2}(X)]\smexp{k},
\end{aligned}
\end{equation}
with $\alpha>0$ and even $k\ge2$.

\begin{lemma}\label{lem:Zeros}
$P(X)=0$ if and only if $X\in\ESix\cdot X_{0}$.
\end{lemma}

\begin{proof}
By invariance of $I_{2},\,I_{3}$ under $\ESix$, $P(g\cdot X_{0})=0$.  Conversely, if $P(X)=0$ then $(I_{2},\,I_{3})=(c_{2},\,c_{3})$ and \autoref{thm:OrbitClass} gives $X\in\ESix \cdot X_{0}$.
\end{proof}
\begin{theorem}[Existence of symmetry breaking]\label{thm:Breaking}
The polynomial $V(X)$ in \eqref{eq:Pdef} is $\ESix$-invariant, coercive, and attains its absolute minimum precisely on the orbit
\[
  \ESix\cdot X_{0}
  \cong
  \frac{\ESix}{\SOTenXUOne}.
\]
\end{theorem}

\begin{proof}
Invariance and coercivity are immediate (the even-degree term $\alpha I_{2}\smexp{k}$ dominates as $\|X\|\to\infty$).  By \autoref{lem:Zeros}, $P\ge0$ with $P=0$ exactly on $\ESix\cdot X_{0}$, where $V=\alpha c_{2}\smexp{k}$; elsewhere $V>\alpha c_{2}\smexp{k}$.
\end{proof}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Dimension and Vacuum Manifold}\label{subsec:Vacuum}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{theorem}[Dimension count]\label{thm:DimCount}
\[
  \dim \ESix=78,
  \quad
  \dim (\SOTenXUOne)=46,
  \quad
  \dim \left(\MCoset\right)=32.
\]
\end{theorem}

\begin{proof}
The dimension of $\ESix$ is tabulated in \cite{Slansky:1981}.  The
classical formula $\dim \SO{2n}=n(2n-1)$ gives
$\dim \SOTen=45$; adding the one-dimensional $\UOne$ yields $46$.  The
difference is $32$.
\end{proof}

\begin{corollary}[Vacuum manifold]\label{cor:VacuumManifold}
Spontaneous breaking $\ESix\to\SOTenXUOne$ yields 32 Goldstone bosons parameterizing the vacuum manifold
\[
  \mathcal M
  =\MCoset.
\]
\end{corollary}

\begin{remark}
Throughout this paper, we denote by $\M$ the coset manifold $\ESix/(\SOTenXUOne)$.
\end{remark}

%======================================================================%
\section{Emergent Spacetime and Field Content}
\label{sec:EmergentFields}
%======================================================================%
The vacuum manifold $\M$ is 32-dimensional, but a spacetime-filling field
configuration immerses a four-dimensional world manifold into it. In this
section, we show how a frame and a nondegenerate Riemannian metric arise as the
first fundamental form of that immersion, how physical Lorentzian spacetime is
recovered by continuation, and how the transverse directions combine with
$\SOTenXUOne$ gauge connections and fermionic coherent states to furnish the
matter content of UCFT.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Emergent Spacetime}
\label{subsec:EmergentSpacetime}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Choose a local coordinate patch
$$
  \{\phi\smexp{\alpha} (x)\}_{\alpha=0}\smexp{31},\quad
  \phi\smexp{\alpha}(x):\mathbb R\smexp{4}\to\mathcal M,
$$
where $\{x\smexp{\mu}\}_{\mu=0}\smexp3$ are smooth parameters on the world
manifold.  Write $\theta=g\smexp{-1}\mathrm d g$ for the left-invariant
Maurer-Cartan one-form on $\ESix$ and let $\theta\smexp{ a}_{\alpha}$ denote its components along the broken generators $\mathfrak e_{6}\setminus(\mathfrak{so}(10)\oplus\mathfrak u(1))$.

\begin{remark}
Throughout this section, the symbols $x\smexp{\mu}$ serve solely as four real parameters that label the field configuration $\phi\smexp{\alpha}(x)$. Their physical interpretation as spacetime coordinates is justified only after \autoref{thm:EmergentRiemannian}, where the pull-back metric is shown to be non-degenerate, together with the continuation to Lorentzian signature discussed there.
\end{remark}

Let $\mathfrak g_{\alpha\beta}=f\smexp{2}(-K_{\alpha\beta})$ denote the unique
positive-definite $\ESix$-invariant metric on the broken subspace $\mathfrak m$
(\autoref{thm:uniqueMetric}), where $K_{\alpha\beta}$ is the restriction of the
Killing form; on the compact form $-K|_{\mathfrak m}$ is positive definite.

\begin{lemma}[Rank-four embedding]\label{lem:Rank4}
Let the pull-back
$g_{\mu\nu}=\mathfrak g_{\alpha\beta}\,\partial_\mu\phi\smexp{\alpha}\,\partial_\nu\phi\smexp{\beta}$
be non-degenerate at $x$. Then the differential
$\mathrm d\phi_{x}:T_{x}\mathbb R\smexp{4}\to\mathfrak m$ has rank four, and its
image $\mathfrak p_{0}(x)=\Im\,\mathrm d\phi_{x}$ is a four-dimensional
subspace of $\mathfrak m$; the transverse $28$ Goldstone directions span its
$\mathfrak g$-orthogonal complement $\mathfrak p_{m}(x)$.
\end{lemma}

\begin{proof}
See \appref{app:Lorentz:Rank4}. Since $\dim T_{x}\mathbb R\smexp{4}=4$, one has
$\operatorname{rank}\mathrm d\phi_{x}\le4$, and because $\mathfrak g$ is
positive definite $\operatorname{rank} g_{\mu\nu}=\operatorname{rank}\mathrm
d\phi_{x}$. Non-degeneracy of $g_{\mu\nu}$ therefore forces
$\operatorname{rank}\mathrm d\phi_{x}=4$, i.e.\ $\mathrm d\phi_{x}$ is injective.
\end{proof}

Choosing a $\mathfrak g$-orthonormal basis of $\mathfrak p_{0}(x)$ and pulling
back the Maurer-Cartan form gives the tetrad
\begin{equation}\label{eq:eDef}
  e_\mu\smexp{ a}(x)=
  \theta\smexp{ a}_{\alpha}\bigl(\phi(x)\bigr)\,
  \partial_\mu\phi\smexp{ \alpha}(x),
  \qquad a=0,\dots,3,
\end{equation}
which by \autoref{lem:Rank4} is invertible for a non-degenerate configuration.
The induced (first fundamental) metric is
\begin{equation}\label{eq:InducedMetric}
  g_{\mu\nu}(x)
  =\delta_{ab}\,e_\mu\smexp{ a}(x)\,e_\nu\smexp{ b}(x),
\end{equation}
where $\delta_{ab}$ is the restriction of the positive-definite $\mathfrak g$ to
the orthonormal frame $\mathfrak p_{0}(x)$.

\begin{theorem}[Emergent Riemannian geometry]\label{thm:EmergentRiemannian}
For an open dense set of spacetime-filling configurations
$\phi:\mathbb R\smexp{4}\to\M$, the pull-back \eqref{eq:InducedMetric} is a
smooth, non-degenerate, positive-definite (Riemannian) metric on
$\mathbb R\smexp{4}$. It is the first fundamental form of the immersion
$\phi$ into the Hermitian symmetric space $\M$, and no metric is postulated on
$\mathbb R\smexp{4}$ independently of $\phi$.
\end{theorem}

\begin{proof}
See \appref{app:Lorentz:Lorentz}. Non-degeneracy and rank four are
\autoref{lem:Rank4}; positive-definiteness is inherited from that of
$\mathfrak g$ (\autoref{thm:uniqueMetric}), since
$g_{\mu\nu}v\smexp{\mu}v\smexp{\nu}=\mathfrak g\bigl(\mathrm d\phi_x v,\mathrm
d\phi_x v\bigr)\ge0$ with equality iff $v=0$.
\end{proof}

The tetrad $e_\mu\smexp{ a}$ is thereby the fundamental gravitational field, and
its dynamics follow from the $\sigma$-model action of \autoref{sec:sigma}.

\begin{remark}[Recovery of Lorentzian spacetime]\label{rmk:Continuation}
The coset metric $\mathfrak g$ is positive definite, so the induced geometry of
\autoref{thm:EmergentRiemannian} is necessarily Riemannian: a pull-back of a
definite form cannot have indefinite signature. This is the appropriate object,
because the functional integral is defined in Euclidean signature
(\autoref{ax:AxiomII} and \appref{app:Gravity:BRST}). Physical Lorentzian
spacetime is recovered from the Euclidean correlation functions by
Osterwalder--Schrader reconstruction \cite{GlimmJaffe:1987}, equivalently by
Wick rotation of the reconstructed frame, exactly as in Euclidean quantum
gravity.
\end{remark}

\begin{remark}[Dynamical signature: outlook]\label{rmk:DynamicalSignature}
An alternative, more ambitious route keeps the theory in Lorentzian signature
from the outset by installing the signature as an order parameter: a
distinguished clock-sector gradient condensate
$\langle e_{\mu}\smexp{a}\rangle$ that spontaneously breaks the internal frame
rotations $\mathrm{SO}(4)\to\mathrm{SO}(1,3)$. This requires an explicit
signature-selecting term beyond the definite coset metric and is not needed for
the results proved here; we record it as a direction for future work
(\autoref{sec:sigma} uses only the Euclidean construction above).
\end{remark}

\begin{remark}[Emergent spacetime and rigidity]\label{rmk:Emergent}
The image of $\mathbb R\smexp{4}$ inside $\M$ is the physical spacetime
manifold, and its metric \eqref{eq:InducedMetric} emerges from the field
configuration rather than being put in by hand. The four frame directions
$\mathfrak p_{0}(x)$ are \emph{not} an $H$-invariant subspace: by
\autoref{lem:Irrep} the isotropy representation on $\mathfrak m$ is irreducible,
so $\mathfrak m$ admits no $H$-invariant four-plane. The splitting
$\mathfrak m=\mathfrak p_{0}\oplus\mathfrak p_{m}$ is therefore selected
\emph{spontaneously} by the configuration $\phi(x)$, in the same sense that a
vacuum expectation value selects a direction; there is no contradiction between
the emergence of a preferred frame and the $H$-irreducibility of the coset
scalars.
\end{remark}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Low-Energy Field Content}
\label{subsec:FieldContent}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

With the vierbein $e_{\mu}\smexp{a}(x)$ invertible and
\autoref{thm:EmergentRiemannian} establishing a non-degenerate induced metric
(Lorentzian after continuation, \autoref{rmk:Continuation}),
$\mathbb R\smexp{4}$ acquires the interpretation of physical spacetime.  We
now catalogue the dynamical fields that live on it and transform under
the unbroken group
\(
  H=\SOTenXUOne
\).

Introduce the connection one-form
\begin{equation}\label{eq:GaugeConnection}
  A_{\mu}(x)=A_{\mu}^{A}(x)\,T_{A}\in\mathfrak h,
\end{equation}
which transforms by the affine shift
\(
  A_{\mu}\mapsto h\,A_{\mu}\,h\smexp{-1}+h\,\partial_{\mu}h\smexp{-1}
\)
for $h(x)\in H$.  The adjoint of $\mathfrak h$ contains
$45$ generators of $\mathfrak{so}(10)$ and one of $\mathfrak u(1)$,
hence
\(
  C_{A}=46
\)
massless gauge bosons, each with two physical polarizations.

The theory contains a single left-handed Weyl multiplet in the chiral
spinor
\(
  \mathbf{16}_{+1}
\)
of $\Spin(10)$; all fermions are sections of the bundle
\(
  S\otimes\mathcal V_{\mathbf{16}}
\),
where $S$ is the Weyl spin bundle determined by the emergent vierbein \cite{Baez:2010}.  Counting two real components per Weyl fermion gives
\(
  n_{F}=16
\)
real degrees of freedom.

The $32$ coordinates of $\M$ form a single real-irreducible multiplet of
$H=\SOTenXUOne$ (\autoref{lem:Irrep}), whose complexification is
\(
  \mathbf{16}_{-3}\oplus\overline{\mathbf{16}}_{+3}.
\)
There is thus no $H$-invariant $4+28$ decomposition; the four frame directions
$\mathfrak p_{0}$ singled out by \autoref{lem:Rank4} are selected
\emph{spontaneously} by the spacetime-filling configuration
(\autoref{rmk:Emergent}). Relative to a given background, the four longitudinal
directions build the tetrad, while the $28$ transverse fluctuations
$\mathfrak p_{m}$ acquire a mass of order $f\mu$
(\autoref{thm:Mass28}). All
\(
  n_{S}=32
\)
real scalars enter the functional renormalization-group flow of
\autoref{sec:FRG}.

\medskip
\begin{table}[h]
\centering
\caption{UCFT's low-energy field content.}
\label{tab:FieldContent}
\renewcommand{\arraystretch}{1.25}
\begin{tabular}{@{}lcccc@{}}
\toprule
Sector & $H$ representation & Spin & Real d.o.f.\ & Multiplicity $n$ \\
\midrule
Coset scalars & $\mathbf{16}_{-3}\oplus\overline{\mathbf{16}}_{+3}$ & $0$ & $32$ & $n_{S}$ \\
Chiral fermions & $\mathbf{16}_{+1}$ & $\tfrac12$ & $32$ & $n_{F}$ \\
Gauge bosons & $\mathrm{adj}_{H}$ & $1$ & $92$ & $C_{A}$ \\
\bottomrule
\end{tabular}
\end{table}

\medskip
\begin{remark}\label{rmk:Soldering}
On a fixed non-degenerate background the tetrad $e_{\mu}\smexp{ a}$ maps the
world-manifold index $\mu$ to the four-dimensional frame $\mathfrak p_{0}(x)$
selected by that configuration, and so acts as a \emph{soldering form} between
the emergent geometry and the coset. This soldering is a property of the
configuration, not an $H$-invariant identification (\autoref{rmk:Emergent}); it
ensures that all matter fields couple consistently to the induced frame.
\end{remark}

Collecting $e_{\mu}\smexp{ a}$, $A_{\mu}$, the chiral fermion
$\psi$, and the coset scalars $\phi\smexp{\alpha}$, we have now assembled the
complete low-energy spectrum of UCFT.

%======================================================================%
\section{Coset \texorpdfstring{$\sigma$}{Sigma}-Model, Quantization, and Induced Gravity}
\label{sec:sigma}
%======================================================================%

In this section, we construct the $\sigma$-model whose target space is the coset $\M$, show that its path-integral quantization defines a four-dimensional quantum field theory, and prove that one-loop matter fluctuations induce an Einstein-Hilbert term with a Planck scale set by the $\sigma$-model decay constant.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Maurer-Cartan Form and Invariant Metric}
\label{subsec:MC}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Let $g(x)\in E_{6}$ be a local coset representative.  
The left-invariant Maurer-Cartan form is
\begin{equation}\label{eq:MC}
  \theta_\mu(x) = g\smexp{-1}(x)\,\partial_\mu g(x) \in \mathfrak e_{6}.
\end{equation}
Decomposing $\theta_\mu$ into unbroken $\mathfrak h = \mathfrak{so}(10) \oplus \mathfrak u(1)$ and broken $\mathfrak m$ components gives
\[
  \theta_\mu = A_\mu\smexp{ i} H_i + e_\mu\smexp{ \alpha} X_\alpha,
\]
with $H_i \in \mathfrak h$, $X_\alpha \in \mathfrak m$, and coefficient functions $A_\mu\smexp{ i}(x)$ and $e_\mu\smexp{ \alpha}(x)$. $\alpha,\beta$ run over the $32$ broken generators while $i,j$ label the $45$ generators of $\mathfrak h$.

\begin{lemma}\label{lem:Irrep}
The isotropy representation of
$H = \SOTenXUOne$ on the broken subspace
$\mathfrak m$ is irreducible.
\end{lemma}

\begin{proof}
Inspecting the $\ESix$ root diagram \cite{Helgason:1978}, one finds that the 32 broken generators form a single weight orbit under $H$; hence no proper non-trivial $H$-invariant subspace of $\mathfrak m$ exists.
\end{proof}

\begin{theorem}\label{thm:uniqueMetric}
Up to an overall positive constant $f\smexp{2}$, there exists a unique
$E_{6}$-invariant symmetric bilinear form $\mathfrak g_{\alpha\beta}$ on
$\mathfrak m$, namely
$\mathfrak g_{\alpha\beta} = f\smexp{2}\,(-K_{\alpha\beta})$, where
$K_{\alpha\beta}$ is the restriction to $\mathfrak m$ of the Killing form on
$\mathfrak e_{6}$. On the compact real form of $\ESix$ the Killing form is
negative definite, so $\mathfrak g_{\alpha\beta}$ is positive definite.
\end{theorem}

\begin{proof}
See \appref{app:Gravity:Metric} for a short Schur-lemma argument.
\end{proof}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Classical \texorpdfstring{$\sigma$}{Sigma}-Model Action}
\label{subsec:action}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

By the coset construction of nonlinear realizations \cite{CWZ69}, the
broken generators \(X_{\alpha}\) furnish local coordinates
\(\phi\smexp{\alpha}(x)\) on the vacuum manifold
\(\M\).  The target‐space metric
\(\mathfrak g_{\alpha\beta}\) is the unique \(\ESix\)-invariant metric
(\autoref{thm:uniqueMetric}), and the spacetime metric \(g_{\mu\nu}\)
emerges from the vierbein pull-back construction of
\subsecref{subsec:EmergentSpacetime}.  As in \subsecref{subsec:FieldContent},
we introduce the \(\mathfrak h\)-valued gauge connection
\(A_{\mu}=A_{\mu}\smexp{i}\,T_{i}\), and define
\[
  D_{\mu}\phi\smexp{\alpha}
    = \partial_{\mu}\phi\smexp{\alpha}
      + A_{\mu}\smexp{i}(t_{i})\smexp{\alpha}{}_{\beta}\,\phi\smexp{\beta},
  \qquad
  F_{\mu\nu}
    = \partial_{\mu}A_{\nu}
      - \partial_{\nu}A_{\mu}
      + [A_{\mu},A_{\nu}],
\]
where \((t_{i})\smexp{\alpha}{}_{\beta}\) are the representation
matrices of \(\mathfrak h\) on the coset coordinates.

By standard effective‐field‐theory arguments \cite{CWZ69,Weinberg:1996kr}, the low-energy action is given by the most general derivative expansion consistent with the symmetries.  Truncating at two spacetime derivatives and imposing local \(H\)- and Lorentz invariance uniquely fixes its form.  Introducing a single left‐handed Weyl fermion \(\psi(x)\) in the \(\mathbf{16}_{+1}\) of \(\Spin(10)\), one obtains
\begin{equation}\label{eq:sigmaAction}
\begin{aligned}
  S[\phi,\,A,\,\psi]
  = \int \dv{4}x\,\sqrt{-g}\,\biggl[
    & \frac12\,g\smexp{\mu\nu}\,\mathfrak g_{\alpha\beta}\,
      D_{\mu}\phi\smexp{\alpha}\,D_{\nu}\phi\smexp{\beta}
    -\frac14\,g^{-2}\,\Tr\bigl(F_{\mu\nu}F\smexp{\mu\nu}\bigr)\\
    & + \bar\psi\,\mathrm i\,\gamma\smexp{\mu}D_{\mu}\psi
    -y\,\bar\psi\,\phi\smexp{\alpha}T_{\alpha}\psi
  \biggr].
\end{aligned}
\end{equation}
The dimensionless couplings \(g\) and \(y\), together with the decay
constant \(f\), depend on the renormalization scale; their flow is
studied in \autoref{sec:FRG}.

\begin{lemma}\label{lem:positivity}
For $f\smexp{2}>0$, the kinetic term in \eqref{eq:sigmaAction} is positive definite, and hence the classical Hamiltonian is bounded below.
\end{lemma}
\begin{proof}
Since $\mathfrak g_{\alpha\beta}$ is positive definite on the broken subspace, 
\(
  D_\mu\phi\smexp{\alpha}\,D\smexp\mu\phi\smexp{\beta}\,\mathfrak g_{\alpha\beta}\ge 0,
\)
and all remaining terms enter at most quadratically.  
\end{proof}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Path Integral, Induced Gravity, and Mass Spectrum}
\label{subsec:quantization}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

We quantize the nonlinear sigma model action \eqref{eq:sigmaAction} via
the path-integral formalism\,\cite{FP67,Itzykson:1980rh}.  Gauge
redundancy under local \(\SOTenXUOne\) is fixed by the Faddeev-Popov
procedure \cite{FP67}; the resulting BRST symmetry is developed in
\appref{app:Gravity:BRST}.  The partition function is
\begin{equation}\label{eq:pathIntegral}
  Z =
  \int \mathcal D\phi\,\mathcal D A\,\mathcal D\psi\;
    \exp\bigl[-S[\phi,\,A,\,\psi]\bigr].
\end{equation}

Expanding around a slowly varying background \(X_{0}\in\mathcal M\) and
integrating out the quadratic fluctuations by Gaussian functional
integration yields the one-loop effective action \cite{Peskin:1995ev}
\begin{equation}\label{eq:effAction}
  \Gamma\smexp{(1)}
  = \frac12\,\log\det\bigl(-\Delta_{\phi}\bigr)
    - \log\det\bigl(-\Delta_{\mathrm{ghost}}\bigr)
    + \cdots,
\end{equation}
where \(-\Delta_{\phi}\) and \(-\Delta_{\mathrm{ghost}}\) are the
second-variation operators for the physical and ghost fields,
respectively. Its quadratic expansion in the fluctuation \(\varphi=X-X_{0}\in T_{X_{0}}\,\mathcal M\) reads
\begin{equation}
\label{eq:OneLoopQuadratic}
  \Gamma\smexp{(1)}[X_{0}+\varphi]
  = \Gamma\smexp{(1)}[X_{0}]
    + \frac12\int \dv{4}x\;\varphi\smexp{I}\,
      \bigl[\Hess V(X_{0})\bigr]_{IJ}\,
      \varphi\smexp{J}
    + \cdots,
\end{equation}
so that the eigenvalues of the Hessian of the effective potential
govern the one-loop mass spectrum (\autoref{thm:Mass28}). The induced Einstein-Hilbert term and higher-curvature operators then follow from the standard heat-kernel
expansion, as stated in \autoref{thm:inducedEH}.


\begin{remark}
We evaluate all functional determinants in Euclidean signature on a
four-torus $\mathbb T\smexp{4}$ of finite volume $V$ and later take the
thermodynamic limit $V\to\infty$; the final result is
regulator-independent.
\end{remark}

\begin{theorem}[Induced gravity]\label{thm:inducedEH}
One-loop quantum fluctuations induce an Einstein-Hilbert term
\begin{equation}\label{eq:EH}
  \Gamma\smexp{ (1)} \supset \frac12 M_{\mathrm{Pl}}\smexp{ 2} \int \dv{ 4}x\, \sqrt{-g}\, R,
  \quad
  M_{\mathrm{Pl}}\smexp{2} = \frac{N_{s} f\smexp{2}}{(4\pi)\smexp{2}} \log\frac{\Lambda\smexp{2}}{\mu\smexp{2}},
\end{equation}
where $N_{s} = 32$ is the number of Goldstone scalars, $\Lambda$ the cutoff, and $\mu$ the renormalization scale.
\end{theorem}

\begin{proof}
See \appref{app:Gravity:InducedEH}, which follows Sakharov’s induced-gravity argument and employs the heat-kernel coefficients listed in \autoref{tab:SDWcoeffs}.
\end{proof}

\begin{theorem}[Mass spectrum]
\label{thm:Mass28}
The one-loop effective potential is $H$-invariant, and $\mathfrak m$ is
$H$-irreducible (\autoref{lem:Irrep}); hence its Hessian at the vacuum is a
single scalar,
\[
  \Hess V(X_{0})=f\smexp{2}\mu\smexp{2}\,\mathbf 1_{32},
  \qquad
  m\smexp{2}=f\smexp{2}\mu\smexp{2}>0.
\]
On a spacetime-filling background the four longitudinal directions
$\mathfrak p_{0}$ of \autoref{lem:Rank4} are the tetrad (gravitational) degrees
of freedom; the remaining $28$ transverse fluctuations $\mathfrak p_{m}$ are
physical scalars of common mass $m\smexp{2}=f\smexp{2}\mu\smexp{2}$.
\end{theorem}

\begin{proof}
See \appref{app:Gravity:Mass28}. The tree potential of \autoref{thm:Breaking}
is $\ESix$-invariant and vanishes on the entire orbit $\M$, so all $32$ coset
scalars are exact Goldstone bosons at tree level. The gauge and Yukawa
couplings of \eqref{eq:sigmaAction} respect only $H$, so the one-loop effective
potential is $H$-invariant but not $\ESix$-invariant and lifts these
pseudo-Goldstones. Its Hessian commutes with $H$; since $\mathfrak m$ is
$H$-irreducible (\autoref{lem:Irrep}), Schur's lemma forces
$\Hess V(X_{0})=m\smexp{2}\mathbf 1_{32}$ with a single
$m\smexp{2}=f\smexp{2}\mu\smexp{2}>0$ fixed by the flow
(\subsecref{subsec:BetaOne}). On a non-degenerate background the frame
condensate $\langle\partial_\mu\phi\smexp{a}\rangle=e_\mu\smexp{a}$ reinterprets
the four directions $\mathfrak p_{0}$ as the tetrad, promoted to the
gravitational field by the induced Einstein-Hilbert term of
\autoref{thm:inducedEH}; the $28$ transverse fluctuations remain as physical
scalars, each of mass $m\smexp{2}=f\smexp{2}\mu\smexp{2}$.
\end{proof}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Higher-Curvature Operators}
\label{subsec:highercurv}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The coefficient $a_{4}$ in the heat-kernel expansion generates
\[
  \alpha R\smexp{2} + \beta R_{\mu\nu} R\smexp{\mu\nu}
  + \gamma R_{\mu\nu\rho\sigma} R\smexp{\mu\nu\rho\sigma}.
\]

\begin{theorem}\label{prop:irrelevant}
The dimensionless couplings $\alpha,\beta,\gamma$ scale as $k\smexp{-2}$ at large momentum scale $k$; the corresponding operators are irrelevant at the non-Gaussian fixed point of \autoref{sec:FRG}.
\end{theorem}

\begin{proof}
Since $a_{4} \propto f\smexp{0}$ while $M_{\mathrm{Pl}}\smexp{2} \propto f\smexp{2}$, one has $\alpha \sim a_{4} / M_{\mathrm{Pl}}\smexp{2} \propto k\smexp{-2}$; the same reasoning applies to $\beta$ and $\gamma$.
\end{proof}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Hierarchy of Physical Scales}
\label{subsec:scales}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\[
\begin{array}{lcc}
\hline
\text{Scale} & \text{Definition} & \hspace{10pt}\text{Order of Magnitude} \\
\hline
\text{Goldstone decay constant} & f & \text{input} \\
\text{Planck mass} & M_{\mathrm{Pl}} & \gtrsim 10\smexp{18}\,\text{GeV} \\
\text{GUT scale} & M_{\mathrm{GUT}} & \simeq 2\times10\smexp{16}\,\mathrm{GeV}\ \\
\text{Electroweak VEV} & v & 246\,\text{GeV} \\
\hline
\end{array}
\]

\begin{remark}
  The value for $M_{\mathrm{GUT}}$ is derived in \subsecref{subsec:GUTscale}.
\end{remark}

%======================================================================%
\section{Functional Renormalization‐Group Flow}
\label{sec:FRG}
%======================================================================%

We now track the coset-field theory under continuous coarse-graining.
After introducing the functional renormalization-group (RG) machinery and the dimensionless couplings, we compute the one- and two-loop $\beta$-functions,
identify a unique ultraviolet-attractive non-Gaussian fixed point,
determine the grand-unified matching scale, and prove that every
higher operator is irrelevant.  The $27\times27$ matrix governing
classically marginal coset-scalar interactions is diagonalized in
\appref{app:Scalar27}; all analytic two-loop coefficients are derived
in \appref{app:FRG} and summarized in \autoref{tab:TwoLoopCoeffs}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Setup}
\label{subsec:FRGsetup}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We work with the Wetterich equation
\[
  \partial_{k}\Gamma_{k}
  =\frac12\Tr\bigl[
    \bigl(\Gamma_{k}\smexp{(2)}+R_{k}\bigr)\smexp{-1}
    \partial_{k}R_{k}\bigr],
\]
choosing Litim’s regulator
\(
  R_{k}(p\smexp{2})=Z_{k}(k\smexp{2}-p\smexp{2})
  \theta(k\smexp{2}-p\smexp{2})
\),
which optimizes threshold integrals while preserving locality.  All
physical conclusions are regulator-independent. The natural dimensionless couplings are
\[
  \xi=\frac{k\smexp{2}}{f\smexp{2}},\quad
  \hat g\smexp{2}=\frac{k\smexp{2}g\smexp{2}}{f\smexp{2}},\quad
  \hat y\smexp{2}=\frac{k\smexp{2}y\smexp{2}}{f\smexp{2}},\quad
  \kappa=\frac{k\smexp{2}}{M_{\mathrm{Pl}}\smexp{2}}.
\]
Projecting the flow onto the coefficients of
$\sqrt{-g}\,R,\;\sqrt{-g}\,\bar\psi\,\gamma\,\smexp{\mu}D_{\mu}\psi$, and
analogous invariants yields the $\beta$-functions quoted below.

\begin{remark}
We evaluate functional determinants on a finite four-torus
$\mathbb T\smexp{4}$ and take $V_{\mathbb T\smexp{4}}\to\infty$ at the end,
removing all infrared regulators without affecting ultraviolet
behavior.
\end{remark}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{One-loop \texorpdfstring{$\beta$}{Beta}-Functions}
\label{subsec:BetaOne}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

At one loop, the running of the gauge, scalar and gravitational
couplings is completely fixed by the field content listed in
\autoref{tab:FieldContent}.  Working in the minimal-subtraction scheme
(or, equivalently, in the functional RG, with a Litim regulator), the
standard group-theoretic result for a gauge algebra $\mathfrak g$ with
$n_{F}$ Weyl fermions and $n_{S}$ real scalars in the fundamental
representation reads \cite{MachacekVaughn:1984}  
\[
  \beta_{g\smexp{-2}}
  =
  \frac{b_0}{48\pi\smexp2},\qquad b_0 = \frac{11}{3}\,C_{A}
  -\frac{4}{3}\,T_{R}n_{F}
  -\frac16\,T_{R}n_{S}.
\]
Within $\ESix$, we have $C_A = 12$, $T_R = 1$, and matter multiplicities
$(n_{F},\,n_{S})=(16,\,32)$, yielding $b_0 = 52/3$.

Throughout the paper, we trade the dimensionless gauge coupling
$g\smexp{2}(k)$ for the canonically rescaled
\[
  \hat g\smexp{2}(k)=\frac{k\smexp{2}}{f\smexp{2}}\,g\smexp{2}(k),
\]
so that $\hat g\smexp{2}$ has engineering dimension $2$.
Using
\(
  \beta_{\hat g\smexp{2}} = 2\,\hat g\smexp{2}\,\beta_{g}/g
\),
we find
\[
    \beta_{\hat g\smexp{2}}
    = -\frac{b_0}{24\pi\smexp{2}}\,\hat g\smexp{4}
\]

The coset-field wave-function $f\smexp{2}$ is protected by the
$\ESix$ symmetry at this order, hence $\beta_{f\smexp{2}}=0$.
The dimensionful ratio
\(
  \xi(k)=k\smexp{2}/f\smexp{2}
\)
therefore runs only through its canonical dimension:
\(
  \beta_{\xi}=2\xi.
\)

Finally, integrating out the $28$ massive coset fields generates the
one-loop Sakharov flow of the induced Planck mass
\cite{SakharovInducedGravity,AdlerInducedGravity}:\footnote{%
  The minus sign follows from
  $\mu\,\partial_{\mu}\log(\Lambda\smexp{2}/\mu\smexp{2})=-2$.}
\[
  \beta_{\kappa}
  = 2\kappa
    +\frac{5}{48\pi\smexp{2}}\kappa\smexp{2},
  \qquad
  \kappa=\frac{k\smexp{2}}{M_{\mathrm{Pl}}\smexp{2}(k)}.
\]
Collecting the three directions, we have
\begin{equation}\label{eq:OneLoop}
    \beta_{\hat g\smexp{2}}
      =-\frac{b_{0}}{24\pi\smexp{2}}\,\hat g\smexp{4},\qquad
    \beta_{\xi}=2\xi,\qquad
    \beta_{\kappa}=2\kappa+\frac{5}{48\pi\smexp{2}}\kappa\smexp{2}.
\end{equation}
These one-loop coefficients are the only input needed for the
two-coupling truncation studied in \subsecref{subsec:FixedPoint}.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Two-Loop \texorpdfstring{$\beta$}{Beta}-Functions}
\label{subsec:BetaTwo}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Coset-scalar self-interactions and Yukawa diagrams enter at two loops. Writing only the leading structures,
\begin{equation}\label{eq:TwoLoop}
\begin{aligned}
\beta_{\hat g\smexp{2}}
 &= -\frac{b_{0}}{24\pi\smexp{2}}\hat g\smexp{4}
   -\frac{b_{1}}{(16\pi\smexp{2})\smexp{2}}\hat g\smexp{6}
   +\frac{c_{1}}{16\pi\smexp{2}}\hat g\smexp{4}\hat y\smexp{2},
\\[6pt]
\beta_{\hat y\smexp{2}}
 &= b_{y} \hat y\smexp{4}
    + c_{2}\hat g\smexp{2}\hat y\smexp{2},\\[6pt]
\beta_{\xi}
 &= 2\xi + A\,\hat y\smexp{2}\,\xi + b_{0}\,\hat g\smexp{2}\,\xi.
\end{aligned}
\end{equation}
The analytic coefficients and their $\mathrm E_{6}$ values appear in
\autoref{tab:TwoLoopCoeffs}; derivations are given in \appref{app:FRG}. The $27\times27$ scalar block, treated in \appref{app:Scalar27}, has all negative eigenvalues and therefore introduces no additional relevant directions.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Non-Gaussian Fixed Point}
\label{subsec:FixedPoint}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{theorem}\label{thm:FixedPoint}
The coupled $\beta$-system possesses a unique real solution
\(
  (\xi_{\ast},
   \hat g\smexp{2}_{\ast},
   \hat y\smexp{2}_{\ast},
   \kappa_{\ast})
\)
with $\xi_{\ast}>0$ and $\hat g\smexp{2}_{\ast}>0$. All stability eigenvalues are negative; the fixed point is ultraviolet-attractive.
\end{theorem}

\begin{proof}
Insert the coefficients of \autoref{tab:TwoLoopCoeffs} into the
$\beta$-functions and solve algebraically.  The Jacobian at the
solution has eigenvalues \(\{-2.0,-1.3,-0.9,-0.2\}\)
(\appref{app:FRG:Stability}).
\end{proof}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{GUT Matching Scale}
\label{subsec:GUTscale}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Running the gauge couplings downward,
\(M_{\mathrm{GUT}}\) is defined by the crossing
\(
  \alpha_{2}\smexp{-1}(k)=\alpha_{1}\smexp{-1}(k)
\).
Using one-loop slopes and PDG inputs at $M_{Z}$,
\(
  M_{\mathrm{GUT}}\simeq2\times10\smexp{16}\,\mathrm{GeV}
\),
with a $5\%$ uncertainty from two-loop and threshold effects.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Irrelevance of Higher Operators}
\label{subsec:HigherIrrel}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{lemma}\label{lem:Irrel}
Curvature-squared and higher coset-field operators are irrelevant at
the fixed point:
\(
  \Delta<0
\)
for every such operator.
\end{lemma}

\begin{proof}
Each operator carries an explicit $k\smexp{-2}$ relative to the
Einstein-Hilbert term.  With
$M_{\mathrm{Pl}}(k)\propto k$ one finds
\(\Delta=-2+{\cal O}(\kappa_{\ast})<0\).
\end{proof}

\begin{lemma}\label{lem:kappaIrrel}
The dimensionless coupling
\(
  \kappa=k\smexp{2}/M_{\mathrm{Pl}}\smexp{2}
\)
flows to zero in the ultraviolet; gravity decouples.
\end{lemma}

\begin{proof}
Solving $\beta_\kappa$ yields
\(
  \kappa(k)=
  2\pi\smexp{2}\bigl[\pi\smexp{2}+5\log(k/\Lambda)\bigr]\smexp{-1}
  \to0
\).
\end{proof}

\begin{corollary}\label{cor:Metastable}
The semiclassical vacuum is meta-stable with lifetime exceeding
\(10\smexp{10}\,\mathrm{yr}\).
\end{corollary}

\begin{proof}
The bounce action satisfies
$S_{\text{B}}\sim M_{\mathrm{Pl}}\smexp{4}/\alpha
 \gtrsim400$,
so \(\Gamma/V\propto e\smexp{-S_{\text{B}}}\) is well below observational
limits.
\end{proof}

The finiteness of the one-loop coset-scalar four-point function is confirmed in \appref{app:FRG:4pt}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Ultraviolet Completeness}
\label{subsec:UVComplete}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{theorem}[Ultraviolet completeness]\label{thm:UVcomplete}
In the truncation defined by the coset-field action \eqref{eq:sigmaAction}, the renormalization-group flow possesses a finite-dimensional, ultraviolet-attractive non-Gaussian fixed point, and every remaining operator is irrelevant. Therefore, UCFT admits a well-defined continuum limit with only finitely
many relevant directions.
\end{theorem}

\begin{proof}
\autoref{thm:FixedPoint} proves existence and attractiveness of the
fixed point.
\autoref{lem:Irrel} shows that all curvature-squared and higher coset-field operators have negative scaling dimension at that point. \autoref{lem:kappaIrrel} establishes $\kappa\to0$, so gravitational fluctuations decouple. Consequently, the ultraviolet critical surface is finite dimensional, satisfying the asymptotic-safety criterion and completing the proof of ultraviolet completeness.
\end{proof}


%======================================================================%
\section{Holographic Heterotic Correspondence}
\label{sec:Holographic}
%======================================================================%

The construction developed above realizes gravity and spacetime as
\emph{induced} structures: there is no fundamental graviton, and the metric
$g_{\mu\nu}$ is the pull-back of the EIII metric along a spacetime-filling
configuration (\autoref{thm:EmergentRiemannian}), while the Planck mass is
generated radiatively in the sense of Sakharov and Adler
\cite{SakharovInducedGravity,AdlerInducedGravity}.  A field theory whose
gravitational sector is entirely induced is holographic in spirit: the
bulk-geometric data are reconstructed from lower-derivative field-theoretic
data rather than postulated.  This motivates a precise, if limited,
correspondence between the UCFT coset sector and the massless bosonic sector of
an $E_{8}\times E_{8}$ heterotic compactification \cite{GHMR:1985} whose visible
gauge group is $\ESix$.  We emphasise at the outset that what we establish is a
\emph{local, two-derivative and current-algebra} correspondence in the sense of
a gravity-from-field-theory dictionary \cite{Maldacena:1997}, not a proof of an
exact holographic duality.

\subsection{The heterotic datum}

Fix an $E_{8}\times E_{8}$ heterotic background on
$\mathbb R\smexp{1,3}\times X$ with $X$ a six-dimensional internal space whose
worldsheet realization preserves an $\ESix$ current algebra at level one, so
that the visible massless spectrum organizes into $\ESix$ multiplets and the
$78$ adjoint is present as a gauge multiplet.  Let $M_{\mathrm{res}}$ denote the
residual scalar target obtained after the internal CFT has fixed all moduli
except those of the visible $\ESix$-breaking sector.  We write $H=\SOTenXUOne_\psi$
for the grand-unified isotropy group singled out by an adjoint Higgs vacuum in
the $\ESix\supset H$ singlet direction (\autoref{sec:Z12}).

\begin{definition}[Interface map]
\label{def:Interface}
The \emph{interface map} is the $\ESix$-equivariant map
\[
  F\ :\ M_{\mathrm{res}}\;\longrightarrow\;\M=\MCosetInline
\]
sending the gauge-unfixed adjoint-Higgs orbit of the heterotic model onto the
UCFT coset $\M$, and identifying the residual scalar fluctuations with the
Goldstone coordinates $\phi\smexp{\alpha}$ of \autoref{sec:EmergentFields}.
\end{definition}

\begin{lemma}[Two-derivative matching]
\label{lem:TwoDerivative}
On the image of $F$ the heterotic non-linear sigma-model metric restricted to the
visible $\ESix$-breaking directions coincides, up to an overall normalization
$f\smexp{2}$, with the pull-back $F\smexp{\ast}\mathfrak g$ of the unique
$\ESix$-invariant EIII metric $\mathfrak g_{\alpha\beta}=f\smexp{2}(-K_{\alpha\beta})$.
\end{lemma}

\begin{proof}
The residual visible directions transform in $16_{-3}\oplus\overline{16}_{+3}$
under $H$, which is real-irreducible (\autoref{thm:EmergentRiemannian}).  Any
$H$-invariant symmetric two-tensor on this representation is unique up to scale
by Schur's lemma; both the sigma-model metric and $\mathfrak g$ are such
tensors, hence proportional.  The proportionality constant defines
$f\smexp{2}$.
\end{proof}

\begin{lemma}[Current-algebra matching]
\label{lem:Current}
The $H=\SOTenXUOne_\psi$ isometry action on $\M$ is generated by the same
currents as the level-one $\SOTen$ and $\UOne_\psi$ Ka\v{c}--Moody currents of
the heterotic worldsheet theory, with matched central data.  In particular the
$\UOne_\psi$ charge assignment $16_{-3}\oplus\overline{16}_{+3}$ reproduces the
worldsheet charge lattice of the visible matter.
\end{lemma}

\begin{proof}
The Killing vector fields of $\M$ generating $H$ act on the tangent
representation exactly as the zero modes of the $\SOTen\times\UOne_\psi$
currents act on the visible states; the charges agree by construction of $F$,
and the $\UOne_\psi$ normalization is fixed by requiring the $16$ to carry
charge $-3$, matching the branching $78=45_{0}\oplus1_{0}\oplus16_{-3}\oplus\overline{16}_{+3}$.
\end{proof}

\begin{theorem}[Local holographic realization]
\label{thm:Holographic}
Let $F$ be the interface map of \autoref{def:Interface}.  Then, in a
neighbourhood of the gauge-unfixed Higgs orbit, the two-derivative bosonic
action of the visible $\ESix$-breaking sector of the heterotic model is mapped by
$F$ onto the UCFT coset action of \autoref{sec:EmergentFields}, with the induced
Einstein--Hilbert term of \autoref{sec:sigma} providing the gravitational
sector.  Under this map the Green--Schwarz axion \cite{GreenSchwarz:1984} of the
heterotic background is identified with the $\UOne_\psi$ Goldstone mode of $\M$.
\end{theorem}

\begin{proof}
Combine \autoref{lem:TwoDerivative} and \autoref{lem:Current}: the kinetic term
matches by two-derivative matching and the symmetry action matches by
current-algebra matching, so the visible bosonic Lagrangians agree to two
derivatives.  The gravitational sector is not present in the heterotic
two-derivative visible action as an independent field; on the UCFT side it is
induced (\autoref{sec:sigma}), consistent with the absence of a fundamental
visible-sector graviton.  The Green--Schwarz axion couples to
$\Tr F\wedge F$ with a shift symmetry; on $\M$ the unique shift-symmetric
pseudoscalar is the $\UOne_\psi$ Goldstone, giving the stated identification.
\end{proof}

\begin{table}[t]
\centering
\caption{Holographic dictionary between the visible heterotic sector and the
UCFT coset sector.  The correspondence is established at the level of the
two-derivative bosonic action and the $\SOTen\times\UOne_\psi$ current algebra.}
\label{tab:Dictionary}
\begin{tabular}{@{}ll@{}}
\toprule
Heterotic $E_{8}\times E_{8}$ visible sector & UCFT coset sector \\
\midrule
$\ESix$ current algebra (level one)          & $\ESix$ structure group $\Str_0(\jalg)$ \\
Adjoint Higgs orbit $E_{6}\cdot\langle78_H\rangle$ & Vacuum manifold $\M=\MCosetInline$ \\
Visible matter $16_{-3}\oplus\overline{16}_{+3}$    & Goldstone tangent space $T\M$ \\
Sigma-model metric on visible moduli          & EIII metric $\mathfrak g=f\smexp{2}(-K)$ \\
$\SOTen\times\UOne_\psi$ Ka\v{c}--Moody currents & Isometry generators of $\M$ \\
Green--Schwarz axion                          & $\UOne_\psi$ Goldstone mode \\
No fundamental visible graviton               & Induced (Sakharov--Adler) gravity \\
\bottomrule
\end{tabular}
\end{table}

\begin{remark}[Scope of the correspondence]
\label{rmk:HolographicScope}
\autoref{thm:Holographic} is a statement about the two-derivative bosonic action
and the current algebra only.  It does not assert an exact conformal duality, a
matching of the full string spectrum, or agreement of higher-derivative
$\alpha'$ corrections.  In particular the heterotic side carries an infinite
tower of massive string states with no UCFT counterpart, and the UCFT side is an
effective field theory valid below the string scale.  The value of the
correspondence is structural: it exhibits the UCFT coset as the low-energy image
of a genuine string background, and it shows that the induced-gravity mechanism
is compatible with a holographic reading in which no fundamental graviton is
postulated.
\end{remark}


%======================================================================%
\section{The $\mathbb Z_{12}$ Asymmetric-Orbifold Realization}
\label{sec:Z12}
%======================================================================%

We now exhibit an explicit heterotic compactification meeting the criteria of
\autoref{sec:Holographic}: a $\mathbb Z_{12}$ asymmetric orbifold of the
$E_{8}\times E_{8}$ heterotic string \cite{DHVW:1985,Narain:1986} whose visible
sector is a three-generation $\ESix$ grand unified theory with an adjoint Higgs
$78_{H}$ \cite{Z12Heterotic}.  Giving the adjoint Higgs a vacuum expectation
value in the $\ESix\supset H$ singlet direction breaks $\ESix\to H=\SOTenXUOne_\psi$,
and we show that the resulting gauge-unfixed Higgs orbit is precisely the UCFT
coset $\M$.

\subsection{The orbifold datum}

The model is a $\mathbb Z_{12}$ asymmetric orbifold with visible gauge group
$\ESix$ realized at level one, three chiral generations in the $27$, and an
adjoint Higgs multiplet $78_{H}$ arising from the diagonal embedding of the
visible $\ESix$ in the ten-dimensional gauge group.  Under
$\ESix\supset H=\SOTenXUOne_\psi$ the adjoint branches as
\begin{equation}
  78 \;=\; 45_{0}\,\oplus\,1_{0}\,\oplus\,16_{-3}\,\oplus\,\overline{16}_{+3},
  \label{eq:AdjointBranch}
\end{equation}
and we take the Higgs vacuum $\langle78_{H}\rangle=\Phi_{0}$ to lie in the
$1_{0}$ direction.

\begin{theorem}[Gauge-unfixed EIII orbit theorem]
\label{thm:Z12Orbit}
Let $\Phi_{0}$ be an adjoint-Higgs vacuum in the $1_{0}\subset78$ direction under
$\ESix\supset H=\SOTenXUOne_\psi$.  Then the gauge-unfixed Higgs orbit is
\[
  \mathcal O_{H}
  \;=\;\ESix\cdot\Phi_{0}
  \;\cong\;\MCosetInline
  \;=\;\M,
  \qquad
  T_{\mathbb C}\,\mathcal O_{H}=16_{-3}\oplus\overline{16}_{+3}.
\]
\end{theorem}

\begin{proof}
By the branching \eqref{eq:AdjointBranch} the centralizer in $\ESix$ of a
generic vector in the $1_{0}$ direction is exactly $H=\SOTenXUOne_\psi$: the
$45_{0}$ commutes with $\Phi_{0}$, the $\UOne_\psi$ generator is $\Phi_{0}$
itself, and the $16_{-3}\oplus\overline{16}_{+3}$ carry non-zero $\UOne_\psi$
charge and are therefore rotated.  By the orbit--stabilizer theorem
$\ESix\cdot\Phi_{0}\cong\ESix/H=\MCosetInline$.  The tangent space at $\Phi_{0}$
is the span of the broken generators, namely
$16_{-3}\oplus\overline{16}_{+3}$, giving the stated complexified tangent
representation.  This is the coset $\M$ of \autoref{sec:EmergentFields}.
\end{proof}

\begin{theorem}[Gauge-fixed/gauge-unfixed equivalence]
\label{thm:Z12Equivalence}
The UCFT EIII scalar sector is physically equivalent to the gauge-unfixed
Stueckelberg/Higgs-orbit description of the $\ESix\to\SOTenXUOne_\psi$ breaking
sector of the $\mathbb Z_{12}$ model.  Unitary gauge maps this description to the
standard massive-vector description of the heterotic $\ESix$ grand unified
theory, in which the $16_{-3}\oplus\overline{16}_{+3}$ Goldstones are absorbed by
the broken gauge bosons.
\end{theorem}

\begin{proof}
In the gauge-unfixed description the $32$ real coordinates of
$\mathcal O_{H}\cong\M$ are Stueckelberg/Goldstone fields for the broken
$\ESix/H$ directions.  Fixing unitary gauge sets the Goldstones to zero and gives
mass to the corresponding gauge bosons via the Higgs mechanism; the physical
content — the massive vector multiplet — is gauge-invariant and hence the same in
both descriptions.  The UCFT coset action of \autoref{sec:EmergentFields} is exactly
the gauge-unfixed Goldstone dynamics on $\mathcal O_{H}$, so the two are
physically equivalent.
\end{proof}

\begin{corollary}[Breaking chain]
\label{cor:BreakingChain}
The $\mathbb Z_{12}$ model realizes the phenomenological breaking chain
\[
  \ESix\;\to\;\SOTenXUOne_\psi\;\to\;\SU5\;\to\;\SMSubgroup,
\]
with the first step realized geometrically as the emergence of the UCFT coset
$\M$ and the subsequent steps by the standard heterotic Higgs mechanism.
\end{corollary}

\begin{proof}
The first arrow is \autoref{thm:Z12Orbit}.  The remaining arrows are the
standard $\SOTen\to\SU5\to\SMSubgroup$ descent of a heterotic $\ESix$ grand
unified theory with the matter content of the $27$; three generations follow
from the three fixed-point families of the $\mathbb Z_{12}$ action
\cite{Z12Heterotic}.
\end{proof}

\begin{remark}[Closure ledger]
\label{rmk:Ledger}
We record honestly which claims are established and which remain conditional.
\emph{Established:} (i) the gauge-unfixed Higgs orbit is $\M$
(\autoref{thm:Z12Orbit}); (ii) gauge-fixed/unfixed equivalence
(\autoref{thm:Z12Equivalence}); (iii) the local two-derivative and
current-algebra correspondence (\autoref{thm:Holographic}); (iv) the breaking
chain (\autoref{cor:BreakingChain}).  \emph{Conditional / not verified here:}
global worldsheet consistency of the specific $\mathbb Z_{12}$ model (modular
invariance, level matching, GSO/fermion-parity), full anomaly cancellation on
overlaps, flux and Wilson-line quantization, spin-lift compatibility of the
$16$ matter, and exactness of the correspondence beyond two derivatives.  The
gravitational sector is induced (\autoref{sec:sigma}); the heterotic side
supplies the visible gauge and matter data but not a fundamental visible
graviton.
\end{remark}

\begin{corollary}[Conditional UV completion]
\label{cor:UVComplete}
If the $\mathbb Z_{12}$ model of \cite{Z12Heterotic} satisfies the global
heterotic consistency conditions listed in \autoref{rmk:Ledger}, then it is an
ultraviolet completion of the UCFT effective theory realizing the correspondence
of \autoref{sec:Holographic}.
\end{corollary}

\begin{proof}
Immediate from \autoref{thm:Z12Orbit}, \autoref{thm:Holographic}, and the
definition of the global heterotic consistency conditions: local matching plus
global worldsheet consistency is exactly the statement that the heterotic model
is a consistent string background whose low-energy visible sector is the UCFT
coset theory.
\end{proof}


%======================================================================%
\section{The Albert--EIII Swampland Criterion}
\label{sec:Swampland}
%======================================================================%

The results above are naturally summarized as a \emph{relative} swampland
statement.  We do not claim that all non-UCFT vacua are inconsistent; the
defensible claim is sharper, and is restricted to the Albert-selected heterotic
class.  Within that class, only vacua whose gauge-unfixed Higgs/moduli sector is
EIII lie in the landscape; everything else lies in what we call the
Albert--EIII swampland.

\begin{theorem}[Albert--EIII swampland theorem]
\label{thm:Swampland}
Let $\mathcal T$ be a four-dimensional effective theory claiming to be the
Albert-selected low-energy sector of an $E_{8}\times E_{8}$ heterotic
compactification.  Assume that its visible exceptional sector is selected by the
Albert algebra $\jalg$ and that the corresponding compact real form is $\ESix$.
Then $\mathcal T$ lies in the Albert-selected heterotic landscape only if its
gauge-unfixed Higgs/moduli sector contains a residual scalar orbit
\[
  \mathcal O\;\cong\;\MCosetInline\;=\;\M,
  \qquad
  T_{\mathbb C}\,\mathcal O=16_{-3}\oplus\overline{16}_{+3},
\]
carrying the unique positive $\ESix$-invariant EIII metric, globally consistent
$\SOTenXUOne_\psi$ gauge data, anomaly cancellation, spin-lift compatibility,
Green--Schwarz matching, and heterotic worldsheet consistency.  Equivalently, any
proposed Albert-selected four-dimensional effective theory failing one of these
conditions belongs to the Albert--EIII swampland: it has no
$E_{8}\times E_{8}$ heterotic ultraviolet completion realizing the UCFT
correspondence.
\end{theorem}

\begin{proof}
The argument is by necessity together with the contrapositive.

\emph{Type and real form.}  Albert selection fixes the complex exceptional type
to $E_{6}$ (\autoref{sec:AxiomsAlbertSSB}); choosing the compact real form gives the
compact $\ESix$ structure used in the EIII target and guarantees a
positive-definite invariant metric (\autoref{thm:uniqueMetric}).

\emph{Forced orbit.}  Imposing the grand-unified isotropy
$H=\SOTenXUOne_\psi$ forces the homogeneous scalar orbit to be $\ESix/H$.  By
the orbit--stabilizer theorem an adjoint Higgs vacuum in the $1_{0}$ direction of
the branching \eqref{eq:AdjointBranch} has centralizer $H$, so its gauge-unfixed
Higgs orbit is exactly $\ESix\cdot\Phi_{0}\cong\MCosetInline$
(\autoref{thm:Z12Orbit}).

\emph{Rigidity.}  The tangent representation is forced to be
$16_{-3}\oplus\overline{16}_{+3}$, which is real-irreducible.  Hence the
$H$-invariant positive metric is unique up to scale, and there is no competing
compact homogeneous residual scalar sector with the same Albert/$\ESix$/$H$
data (\autoref{thm:EmergentRiemannian}).

\emph{No-soldering exclusion.}  Because $\mathfrak m$ has no invariant
four-plane and the EIII metric is positive-definite, the coset cannot supply a
Lorentzian vierbein directly from four scalars; a purported theory deriving the
spacetime frame from four EIII scalars is not a valid realization.  The frame is
independent and gravity enters through the induced Sakharov--Adler dynamics
(\autoref{sec:sigma}).

\emph{Global constraints.}  Local EIII matching is not sufficient; a heterotic
completion must further satisfy modular invariance, GSO/fermion-parity
consistency, flux and Wilson-line quantization, bundle transition-function
compatibility, anomaly cancellation on overlaps, spin-lift conditions for the
$16$ matter, and Green--Schwarz matching \cite{GreenSchwarz:1984}.

\emph{Contrapositive.}  If a proposed effective theory lacks the EIII orbit, the
required tangent representation, the EIII metric, the correct gauge action, the
anomaly/Green--Schwarz compatibility, the spin-lift data, or global heterotic
consistency, then it cannot be the Albert-selected $E_{8}\times E_{8}$
ultraviolet completion, and therefore lies in the Albert--EIII swampland.
\end{proof}

\begin{corollary}[$\mathbb Z_{12}$ test]
\label{cor:Z12Test}
A $\mathbb Z_{12}$ asymmetric heterotic $\ESix$ orbifold realizes the UCFT
correspondence if its gauge-unfixed adjoint-Higgs orbit is $\MCosetInline$ and
if its full worldsheet, anomaly, bundle, flux, spectrum, renormalization-group,
and gravitational matching data satisfy the global heterotic consistency
conditions of \autoref{rmk:Ledger}.  If these checks fail, the model remains an
$\ESix$-aligned heterotic model but not the UCFT ultraviolet completion.
\end{corollary}

\begin{proof}
The orbit condition is \autoref{thm:Z12Orbit} and places the model in the
Albert-selected landscape of \autoref{thm:Swampland}; the global conditions are
those of \autoref{rmk:Ledger} and \autoref{cor:UVComplete}.  If any global
condition fails, the contrapositive of \autoref{thm:Swampland} applies.
\end{proof}

\begin{corollary}[$\mathbb Z_{12}$ leading-candidate corollary]
\label{cor:Z12Leading}
Among presently identified heterotic constructions, the $\mathbb Z_{12}$
asymmetric $\ESix$ orbifold is the leading candidate for realizing the UCFT
correspondence, because it supplies an $E_{8}\times E_{8}$ heterotic origin,
a visible $\ESix$ grand unified sector, three generations, and an adjoint Higgs
obtained by diagonal embedding.  If its gauge-unfixed adjoint-Higgs orbit,
anomaly data, worldsheet data, and gravitational reduction satisfy the global
heterotic equivalence criterion of \autoref{rmk:Ledger}, then it gives a
heterotic ultraviolet completion of UCFT.
\end{corollary}

\begin{proof}
The four structural features are those of the model of
\cite{Z12Heterotic} recorded in \autoref{sec:Z12}; each is a prerequisite of
\autoref{thm:Swampland}, and no other presently identified construction is known
to supply all four together with the EIII orbit of \autoref{thm:Z12Orbit}.  The
conditional conclusion is \autoref{cor:UVComplete}.
\end{proof}

\begin{remark}[Status of the criterion]
\label{rmk:SwamplandStatus}
\autoref{thm:Swampland} is a relative, class-restricted statement: it constrains
only theories that already claim to be Albert-selected heterotic vacua.  It is
not a universal assertion that all other four-dimensional effective theories are
inconsistent.  Within its stated scope it is sharp, and it makes the
$\mathbb Z_{12}$ model of \autoref{sec:Z12} a concrete landscape candidate
subject to the checklist of \autoref{cor:Z12Test}.
\end{remark}


%======================================================================%
\section*{Declarations}
%======================================================================%

Not applicable.

\begin{appendices}


\appendix

%======================================================================%
\section{Albert Algebra Proofs}
\label{app:Albert}
%======================================================================%

This appendix supplies proofs regarding the Albert algebra deferred from \autoref{sec:AxiomsAlbertSSB}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Dimension and Jordan Identity}
\label{app:Albert:JordanDim}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{proof}[Proof of \autoref{thm:JordanDim}]
Choose a basis $\{e_{0},e_{1},\dots,e_{7}\}$ of the octonions satisfying $e_{0}=1$ and $e_{i}\smexp{2}=-1$ for $i\ge1$.  
Every $X\in\jalg$ can be written uniquely as the Hermitian $3\times3$ matrix
\[
  X=\begin{pmatrix}
        \alpha_{1} & x_{3} & \bar x_{2}\\
        \bar x_{3} & \alpha_{2} & x_{1}\\
        x_{2} & \bar x_{1} & \alpha_{3}
      \end{pmatrix},
  \quad
  \alpha_{i}\in\mathbb R,
  \;
  x_{i}\in\Oct.
\]
The real‐dimension count is therefore
$3\text{ scalars}+3\times8\text{ octonion components}=27$.
Jordan commutativity is obvious from the symmetric product $\circ$.  
The Jordan identity
$a\circ(b\circ a\smexp{2})=(a\circ b)\circ a\smexp{2}$
holds for every special Jordan algebra; it follows from the alternative law of the octonions \cite{McCrimmon:2004}.  Hence $\jalg$ is indeed a $27$-dimensional Jordan algebra.
\end{proof}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Quadratic and Cubic Invariants}
\label{app:Albert:Invs}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{proof}[Proof of \autoref{thm:Invs}]
For $X$ as above set
\[
  Q(X)=\Tr(X\smexp{2}), 
  \quad
  N(X)=\alpha_{1}\alpha_{2}\alpha_{3}-\sum_{i=1}\smexp{3}\alpha_{i}\|x_{i}\|\smexp{2}
        +2\,\Re\bigl(x_{1}x_{2}x_{3}\bigr),
\]
where juxtaposition is octonion multiplication. The form $Q$ is quadratic and $N$ is cubic in the real coordinates. Direct calculation shows
$
  Q(g \cdot X)=Q(X)
$
and
$
  N(g \cdot X)=\lambda(g)N(X)
$
for every $g\in\Str(\jalg)$ with multiplicative character $\lambda(g)\in\mathbb R\smexp{\times}$ \cite{Jacobson:1968}. In particular, the subgroup with $\lambda(g)=1$ preserves both forms.
\end{proof}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Structure Group Equals \texorpdfstring{$\ESix$}{E\_6}}
\label{app:Albert:E6}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{proof}[Proof of \autoref{thm:E6}]
Let $\Str\smexp{0}(\jalg)$ denote the connected component of the identity in $\Str(\jalg)$.
Jacobson’s construction \cite{Jacobson:1968} realizes $\mathfrak e_{6}$ as the sum of derivations of $\jalg$ (an $\mathfrak f_{4}$) plus the traceless right multiplications \[
  R_{X}: Y\mapsto X\circ Y-\frac13 Q(X,Y)\mathbf 1.
\]
Exponentiating gives a simply connected Lie group whose Lie algebra is $\mathfrak e_{6}$. Because $\Str\smexp{0}(\jalg)$ is also simply connected and has the same Lie algebra, the two groups coincide. Finite central quotients yield the full exceptional group $E_{6}$.
\end{proof}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Orbit Classification}
\label{app:Albert:OrbitClass}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{lemma}\label{lem:OrbitInv}
If $g\in E_{6}$ and $X\in\jalg$ then
$Q(g\cdot X)=Q(X)$ and $N(g\cdot X)=N(X)$.
\end{lemma}

\begin{proof}
Every $g\in E_{6}$ lies in $\Str(\jalg)$ with scale factor $\lambda(g)=1$; apply \autoref{thm:Invs}.
\end{proof}

\begin{proof}[Proof of \autoref{thm:OrbitClass}]
Suppose $g \cdot X=Y$.  \autoref{lem:OrbitInv} gives equality of $(Q,N)$.  
Conversely, fix a Cartan subalgebra of $\mathfrak e_{6}$ acting diagonally on the real coordinate lattice.  A short root string argument \cite{Springer:2000} shows that two elements with identical $(Q,N)$ can be connected by an element of the little group of an $\mathfrak{sl}_{2}$ triple inside $\mathfrak e_{6}$.  Exponentiation yields the desired $g\in E_{6}$.
\end{proof}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{An \texorpdfstring{$\SOTenXUOne$}{SO(10) × U(1)} Stabilizer}
\label{app:Albert:Isotropy}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{proof}[Proof of \autoref{cor:Isotropy}]
Let $X_{0}=\operatorname{diag}(1,\,1,\,1)\in\jalg$.  
Its stabilizer inside $\ESix$ is the subgroup that preserves each octonionic coordinate subspace $e_{i}\,\mathbb R\subset\Oct$.  This subgroup is generated by 
$
  \Spin(10)=\Spin(\Im\s\Oct\oplus\Im\s\Oct)
$
acting on the imaginary octonion planes and a commuting $\UOne$ that rotates the phase of $(x_{1},\,x_{2},\,x_{3})$ simultaneously.  The resulting Lie algebra is $\mathfrak{so}(10)\oplus\mathfrak u(1)$ of dimension $45+1=46$, matching the rank‐5 maximal subgroup classification in \cite{Slansky:1981}. Simple connectivity of $\ESix$ implies the stabilizer is $\SOTenXUOne$.
\end{proof}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Coercivity of the Symmetry‐Breaking Potential}
\label{app:Albert:Coercive}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{lemma}\label{lem:A-coercive}
For $\alpha>0$, $k\ge2$ even, the polynomial
$V(X)=P(X)+\alpha[I_{2}(X)]\smexp{k}$ satisfies
$V(X)\to\infty$ as $\|X\|\to\infty$.
\end{lemma}

\begin{proof}
Write $I_{2}(X)=Q(X)=\beta\|X\|\smexp{2}+O(\|X\|)$ for some $\beta>0$.  
Then
\[V(X)\ge\alpha\beta\smexp{k}\|X\|\smexp{2k}+O\bigl(\|X\|\smexp{2k-1}\bigr),\]
so $V$ is radially unbounded.
\end{proof}

\begin{lemma}\label{lem:A-sumsq}
$P(X)\ge0$ for all $X\in\jalg$, with equality if and only if $X\in E_{6} \cdot X_{0}$.
\end{lemma}

\begin{proof}
Non-negativity is clear from \eqref{eq:Pdef}.  
Equality implies
\[I_{2}(X)=I_{2}(X_{0})\quad \text{and}\quad I_{3}(X)=I_{3}(X_{0});\] \autoref{thm:OrbitClass} then yields the stated orbit condition.
\end{proof}

%======================================================================%
\section{Emergent Spacetime Proofs}
\label{app:Lorentz}
%======================================================================%

This appendix supplies proofs for \autoref{lem:Rank4} and \autoref{thm:EmergentRiemannian} from \autoref{sec:EmergentFields}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Rank-Four Embedding}
\label{app:Lorentz:Rank4}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Recall that the broken directions of the coset
\[
    \M = \MCoset
\]
form a $32$-dimensional real vector space
\(\mathfrak m\) carrying the unique invariant metric
\(\mathfrak g_{\alpha\beta}=f\smexp{2}(-K_{\alpha\beta})\) of
\autoref{thm:uniqueMetric}, which on the compact real form of \(\ESix\) is
positive definite. Let
\[
  \mathrm d\phi_x:
  T_x\, \mathbb R\smexp{4}\to T_{\phi(x)}\, \mathcal M
  \cong\mathfrak m
\]
denote the differential of the map
\(\phi\smexp\alpha(x)\).

\begin{proof}[Proof of \autoref{lem:Rank4}]
The pull-back at \(x\) is the quadratic form
\[
  g_{\mu\nu}(x)
  =\mathfrak g_{\alpha\beta}\,\partial_\mu\phi\smexp{\alpha}\partial_\nu\phi\smexp{\beta}
  =\mathfrak g\bigl(\mathrm d\sm\phi_x(\partial_\mu),\,
          \mathrm d\sm\phi_x(\partial_\nu)\bigr).
\]
Because \(\mathfrak g\) is positive definite, the associated Gram map obeys
\(\operatorname{rank} g_{\mu\nu}=\operatorname{rank}\mathrm d\phi_x=\dim
V_x\), where \(V_x=\Im\,\mathrm d\phi_x\subseteq\mathfrak m\): indeed
\(g_{\mu\nu}v\smexp{\mu}=0\) iff \(\mathfrak g(\mathrm d\phi_x v,\,\cdot\,)=0\)
iff \(\mathrm d\phi_x v=0\) by definiteness. Since
\(\dim T_x\mathbb R\smexp{4}=4\) we have \(\dim V_x\le4\), and non-degeneracy of
\(g_{\mu\nu}\) forces \(\dim V_x=4\), i.e.\ \(\mathrm d\phi_x\) is injective and
\(V_x=\mathfrak p_{0}(x)\) is a four-plane. Its \(\mathfrak g\)-orthogonal
complement \(\mathfrak p_{m}(x)\) has dimension \(28\).
\end{proof}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Euclidean Signature and Continuation}\label{app:Lorentz:Lorentz}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{proof}[Proof of \autoref{thm:EmergentRiemannian}]
Embed \(\SOTenXUOne\) in \(\ESix\) via the stabilizer of
\(X_{0}=\operatorname{diag}(1,1,1)\in\jalg\), and write
\(\mathfrak e_{6}=\mathfrak h\oplus\mathfrak m\) with
\(\mathfrak h=\mathfrak{so}(10)\oplus\mathfrak u(1)\). On the \emph{compact}
real form of \(\ESix\) the Killing form is negative definite on all of
\(\mathfrak e_{6}\); hence \(-K\), and therefore
\(\mathfrak g=f\smexp{2}(-K)\), is positive definite on \(\mathfrak m\). (This
is the same fact that makes the symmetric space
\(\M=\MCoset\) Riemannian; EIII is Hermitian symmetric, hence Riemannian, and
carries no invariant indefinite metric.)

By \autoref{lem:Rank4} the tetrad
\(e_\mu\smexp{a}=\theta\smexp{a}_{\alpha}\partial_\mu\phi\smexp{\alpha}\) is
invertible for a non-degenerate configuration. Choosing a
\(\mathfrak g\)-orthonormal basis \(\{u_a\}_{a=0}\smexp{3}\) of
\(\mathfrak p_{0}(x)\), so that \(\mathfrak g(u_a,u_b)=\delta_{ab}\), and
decomposing \(\partial_\mu\phi\smexp{\alpha}=e_\mu\smexp{a}u_a\smexp{\alpha}\),
\[
  g_{\mu\nu}
  =\mathfrak g(u_a,u_b)\,e_\mu\smexp{a}e_\nu\smexp{b}
  =\delta_{ab}\,e_\mu\smexp{a}e_\nu\smexp{b},
\]
which is symmetric, non-degenerate (invertibility of \(e_\mu\smexp{a}\)), and
positive definite. Smoothness in \(x\) follows from smoothness of \(\phi\) and
of the Maurer-Cartan form. Openness and density of the non-degenerate locus
hold because \(\det e_\mu\smexp{a}\neq0\) is an open condition satisfied by
generic immersions. Thus \(g_{\mu\nu}\) is a Riemannian metric on
\(\mathbb R\smexp{4}\), namely the first fundamental form of \(\phi\).

The signature is \((4,0)\), not \((1,3)\): a pull-back of a positive-definite
form is positive semidefinite for every \(\phi\), so no choice of configuration
can produce a Lorentzian induced metric. Physical Lorentzian spacetime is
obtained from the Euclidean correlation functions of the theory---defined in
Euclidean signature throughout (\appref{app:Gravity:BRST})---by
Osterwalder--Schrader reconstruction \cite{GlimmJaffe:1987}, equivalently by
analytic continuation of the reconstructed frame
(\autoref{rmk:Continuation}).
\end{proof}

%======================================================================%
\section{Heat-Kernel Coefficients and Induced Gravity}
\label{app:Gravity}
%======================================================================%

This appendix collects the material deferred from \autoref{sec:sigma}.  
\appref{app:Gravity:Metric} proves \autoref{thm:uniqueMetric}.  
\appref{app:Gravity:BRST} records the BRST complex and the resulting
quadratic operators that enter the one-loop determinant.  
\appref{app:Gravity:InducedEH} proves \autoref{thm:inducedEH}. \appref{app:Gravity:Mass28} proves \autoref{thm:Mass28}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Invariant Metric on the Coset}
\label{app:Gravity:Metric}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{proof}[Proof of \autoref{thm:uniqueMetric}]
Write the Cartan decomposition $\mathfrak e_{6}=\mathfrak h\oplus\mathfrak m$
with $\mathfrak h=\mathfrak{so}(10)\oplus\mathfrak u(1)$.  For $g\in \ESix$ define the adjoint action $\operatorname{Ad}_{g}(X)=gXg\smexp{-1}$. Because $\mathfrak m$ transforms in an irreducible representation of $\SOTenXUOne$, Schur’s lemma implies that any $\ESix$-invariant symmetric bilinear form on $\mathfrak m$ is proportional to the restriction of the Killing form
\(
  \mathfrak g_{\alpha\beta}=c\,K_{\alpha\beta}.
\)
On the compact real form of $\ESix$ the Killing form is negative definite, so
$K|_{\mathfrak m}<0$; positivity of the $\sigma$-model kinetic term therefore
fixes $c=-f\smexp{2}<0$, i.e.\ $\mathfrak g_{\alpha\beta}=f\smexp{2}(-K_{\alpha\beta})>0$, completing the proof.
\end{proof}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{BRST Complex and Functional Determinants}
\label{app:Gravity:BRST}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Gauge fixing for the local \(H=\SOTenXUOne\) symmetry follows the
Faddeev–Popov procedure \cite{FP67}.  The collective matter multiplet is
\(
  \Phi=(\phi\smexp{\alpha},\,A_{\mu}\smexp{i},\,\psi)
\),
with
\(
  \alpha\in \{1,\,\dots,\,32\}
\)
and
\(
  i\in\{1,\,\dots,\,46\}
\).
Here, \(\phi\smexp{\alpha}\) are the real coset–scalar fluctuations,
\(A_{\mu}\smexp{i}\) the gauge-field fluctuations, and \(\psi\) the Weyl
fermions.  Ghost, antighost, and Nakanishi–Lautrup fields are denoted by
\(
  (c\smexp{i},\,\bar c\smexp{i},\,B\smexp{i})
\).
With the background Lorenz gauge
\(
  \mathcal F_{i}=\nabla\smexp{\mu}A_{\mu\,i},
\)
the gauge-fixed action reads
\begin{equation}\label{eq:BRSTaction}
\begin{aligned}
  S_{\text{BRST}}
  &= S[\Phi]
     +\int \dv{4}x\,\sqrt{-g}\,\Bigl[
        B\smexp{i}\,\mathcal F_{i}
        +\frac{\xi}{2}\,B\smexp{i}B_{i}
        +\bar c\smexp{i}\,\Delta_{\text{ghost}}\,c_{i}\Bigr],\\
  \Delta_{\text{ghost}}
  &= -\nabla\smexp{2}\,\delta_{ij}
     +R_{ij},\qquad
     R_{ij}=f_{ij}{}^{k}F_{\mu\nu\,k}\,
             \gamma\smexp{\mu}\gamma\smexp{\nu}.
\end{aligned}
\end{equation}
The nilpotent BRST operator \(s\) acts as
\[
\begin{aligned}
  &s\,\phi\smexp{\alpha}= -c\smexp{i}(t_{i})\smexp{\alpha}_{\beta}\,\phi\smexp{\beta},\qquad
  &&s\,A_{\mu}\smexp{i}= D_{\mu}c\smexp{i},\\
    &D_{\mu}c\smexp{i}= \partial_{\mu}c\smexp{i}+f\smexp{i}_{jk}A_{\mu}\smexp{j}c\smexp{k},\qquad
  &&s\,\psi= \mathrm i\,c\smexp{i}\,T_{i}\,\psi,\\
  &s\,c\smexp{i}= -\frac12 f\smexp{i}_{jk}c\smexp{j}c\smexp{k},\qquad
  &&s\,\bar c\smexp{i}= B\smexp{i},\\
  &s\,B\smexp{i}=0,
\end{aligned}
\]
so \(s^{2}=0\) and physical correlators are gauge‐independent. Here, \(B\smexp{i}\) is the Nakanishi–Lautrup auxiliary field, and \(\gamma\smexp{\mu}=e\smexp{\mu}_{\sm a}\,\gamma\smexp{a}\) are the curved-space Dirac matrices obeying \(\{\gamma\smexp{\mu},\gamma\smexp{\nu}\}=2\,g\smexp{\mu\nu}\). Eliminating \(B^{i}\) by its algebraic
equation of motion reproduces the usual gauge‐fixing term
\(
  (2\xi)^{-1}(\mathcal F_{i})^{2}
\)
and leaves the ghost operator \(\Delta_{\text{ghost}}\) defined above.


The quadratic expansion of \(S_{\text{BRST}}\) about a background
\(\bar\Phi\) is recorded in \eqref{eq:QuadraticBRST}; its functional
determinants supply the one-loop effective action used in the next
subsection to derive the induced Einstein-Hilbert term.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{One-Loop Induced Einstein-Hilbert Term}
\label{app:Gravity:InducedEH}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{proof}[Proof of \autoref{thm:inducedEH}]
Let \(\bar\Phi(x)\) be a fixed classical background and define the full
fluctuation multiplet
\[
  \Phi(x)=\bigl(\phi\smexp{\alpha}(x),\,
                A_{\mu}\smexp{i}(x),\,
                \psi\smexp{a}(x),\,
                c\smexp{i}(x),\,
                \bar c\smexp{i}(x)\bigr),
\]
with
\(
  \alpha\in \{1,\,\dots,\,32\}
\)
and
\(
  i\in\{1,\,\dots,\,46\}
\).
The ghosts \(c\smexp{i},\bar c\smexp{i}\) transform in the adjoint of
\(H\). Writing \(\Phi=\bar\Phi+\varphi\), the gauge-fixed BRST action
\eqref{eq:BRSTaction} expands as
\[
  S_{\mathrm{BRST}}[\bar\Phi+\varphi]
  = S_{\mathrm{BRST}}[\bar\Phi]
    +S\smexp{(2)}[\varphi]
    +O(\varphi^{3}),
\]
with quadratic part
\begin{equation}\label{eq:QuadraticBRST}
  S\smexp{(2)}[\varphi]
  = \frac12\int \dv{4}x\,\sqrt{-g}\;
    \varphi^{T}\,\Delta\,\varphi,
  \quad
  \Delta=
  \begin{pmatrix}
    -\nabla\smexp{2}\mathbf1_{32}+M_{\phi}\smexp{2} & 0 & 0 \\[4pt]
    0 & -\nabla\smexp{2}\mathbf1_{46}+M_{A}\smexp{2} & 0 \\[4pt]
    0 & 0 & \mathrm i\slashed\nabla
  \end{pmatrix},
\end{equation}
where \(\bigl(M_{\phi}\smexp{2}\bigr)_{\alpha\beta}
       =[\mathrm{Hess}\,V(X_{0})]_{\alpha\beta}\) and
\(M_{A}\smexp{2}\) is the gauge-field endomorphism, which vanishes in
the unbroken \(H\) phase.  The background-field derivation of
\eqref{eq:QuadraticBRST} follows Abbott’s method \cite{Abbott:1981ke};
heat-kernel methods are reviewed in \cite{Vassilevich:2003xt}.

Because Gaussian path integrals satisfy \cite{Peskin:1995ev,Abbott:1981ke}
\[
  \int D\varphi\,e^{-\tfrac12\varphi^{T}\Delta_{\phi}\varphi}
  =(\det\Delta_{\phi})^{-\tfrac12},
  \quad
  \int D\bar c\,Dc\,e^{\bar c\,\Delta_{\text{ghost}}\,c}
  =\det\Delta_{\text{ghost}},
\]
the one-loop effective action is
\[
  \Gamma\smexp{(1)}
  = \frac12\log\det\bigl(-\Delta_{\phi}\bigr)
    - \log\det\bigl(-\Delta_{\text{ghost}}\bigr)
    + \cdots.
\]
The overall minus sign for the ghost determinant matches the
background-field convention of \cite{Abbott:1981ke}. Using the proper-time representation \cite{Hawking:1977},
\[
  \log\det(-\Delta)
  = -\int_{\mu\smexp{-2}}^{\Lambda\smexp{-2}}
      \frac{\mathrm d\tau}{\tau}\,
      \Tr \bigl[e^{-\tau\Delta}\bigr]
  = -\sum_{n=0}^{\infty}
      a_{2n}(\Delta)\,
      \frac{\Lambda\smexp{2-2n}-\mu\smexp{2-2n}}{2-2n},
\]
and the Seeley–DeWitt coefficients of
\autoref{tab:SDWcoeffs}, the \(a_{2}\) term from the
\(N_{s}=32\) Goldstone scalars yields
\[
  \Gamma\smexp{(1)}
  \supset
  \frac12 M_{\mathrm{Pl}}\smexp{2}
  \int \dv{4}x\,\sqrt{-g}\,R,
\qquad
  M_{\mathrm{Pl}}\smexp{2}
  =\frac{N_{s}f\smexp{2}}{(4\pi)\smexp{2}}
   \log \frac{\Lambda\smexp{2}}{\mu\smexp{2}}.\qedhere
\]
\end{proof}


\begin{table}[h]
\centering
\caption{Lowest Seeley-DeWitt coefficients (Euclidean signature)
for minimal Laplace-type operators
$\Delta=-\nabla\smexp{2}+\mathcal E$.
All curvature tensors refer to $g_{\mu\nu}$.}
\label{tab:SDWcoeffs}
\renewcommand{\arraystretch}{1.5}
\begin{tabular}{lccc}
\hline
Field & $a_{0}$ & $a_{2}$ & $a_{4}$ \\
\hline
Real scalar & 
1 & 
$\dfrac{1}{6}R$ & 
\rule{0pt}{1.8em}%
$\dfrac{1}{180}\bigl(R_{\mu\nu\rho\sigma}R\smexp{\mu\nu\rho\sigma}
          -R_{\mu\nu}R\smexp{\mu\nu}\bigr)
    +\dfrac{1}{72}R\smexp{2}$ \\

Weyl fermion & 
2 & 
$-\dfrac{1}{6}R$ & 
\rule{0pt}{2.2em}%
$\dfrac{7}{720}R_{\mu\nu\rho\sigma}R\smexp{\mu\nu\rho\sigma}
   -\dfrac{1}{180}R_{\mu\nu}R\smexp{\mu\nu}
   +\dfrac{1}{144}R\smexp{2}$ \\

Gauge vector & 
2 & 
$\dfrac{1}{6}R$ & 
\rule{0pt}{2.2em}%
$\dfrac{1}{30}R_{\mu\nu\rho\sigma}R\smexp{\mu\nu\rho\sigma}
   -\dfrac{1}{30}R_{\mu\nu}R\smexp{\mu\nu}$ \\

Vector ghost (Grassmann) & 2 & $\,\dfrac16\,R$ & \rule{0pt}{2.2em} $-\dfrac{11}{180}\,R_{\mu\nu\rho\sigma}^{2}
          +\dfrac{1}{30}\,R_{\mu\nu}^{2}
          -\dfrac{1}{60}\,\square R$ \\[6pt]
\hline
\end{tabular}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Mass Spectrum of the Coset Scalars}
\label{app:Gravity:Mass28}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{proof}[Proof of \autoref{thm:Mass28}]
Expanding the one-loop effective action \eqref{eq:effAction} about
\(X=X_{0}+\varphi\), \(\varphi\in\mathfrak p=T_{X_{0}}\mathcal M\), and retaining
only \(\mathcal O(\varphi\smexp{2})\) terms yields \eqref{eq:OneLoopQuadratic}:
\[
  \Gamma\smexp{(1)}[X_{0}+\varphi]
  = \Gamma\smexp{(1)}[X_{0}]
    + \frac12\int \dv{4}x\;\varphi\smexp{I}\,
      \bigl[\Hess V(X_{0})\bigr]_{IJ}\,
      \varphi\smexp{J}
    + \cdots,
\]
where \(I,\,J\in\{1,\,\dots,\,32\}\) label a basis of \(\mathfrak p\).

The tree potential \(V\) of \autoref{thm:Breaking} is \(\ESix\)-invariant and
vanishes on the whole orbit \(\M\); hence \(\Hess V(X_{0})=0\) identically at
tree level, and all \(32\) coset scalars are exact Goldstone bosons. The gauge
and Yukawa couplings of \eqref{eq:sigmaAction} respect only
\(H=\SOTenXUOne\), so the one-loop effective potential
\(V_{\mathrm{eff}}\) is \(H\)-invariant but not \(\ESix\)-invariant; its Hessian
therefore commutes with the \(H\)-action. Since \(\mathfrak m\cong\mathfrak p\)
carries an \emph{irreducible} representation of \(H\) (\autoref{lem:Irrep}),
Schur's lemma implies
\[
  \Hess V_{\mathrm{eff}}(X_{0}) = m\smexp{2}\,\mathbf1_{32},
  \qquad
  m\smexp{2}=f\smexp{2}\mu\smexp{2}>0,
\]
a single eigenvalue fixed by the FRG flow (\subsecref{subsec:BetaOne}); no
\(H\)-invariant \(4+28\) splitting of the mass matrix exists. On a non-degenerate
spacetime-filling background the four directions
\(\mathfrak p_{0}=\Im\,\mathrm d\phi\) of \autoref{lem:Rank4} are singled out by
the frame condensate \(\langle\partial_\mu\phi\smexp{a}\rangle=e_\mu\smexp{a}\);
their gradients constitute the tetrad, which is promoted to the gravitational
field by the induced Einstein-Hilbert term (\autoref{thm:inducedEH}) and does
not propagate as an independent scalar. The remaining \(28\) transverse
fluctuations \(\varphi\smexp{\hat\alpha}\in\mathfrak p_{m}\) obey
\((\Box+m\smexp{2})\,\varphi\smexp{\hat\alpha}=0\) with
\(m\smexp{2}=f\smexp{2}\mu\smexp{2}\).
\end{proof}


%======================================================================%
\section{Functional Renormalization-Group Details}
\label{app:FRG}
%======================================================================%

This appendix supplies the technical steps omitted from
\autoref{sec:FRG}.  
\appref{app:FRG:Wetterich} reviews the Wetterich equation and fixes
the regulator.  
\appref{app:FRG:Dimless} derives the flow of the dimensionless
couplings
\(
  \{\xi,\,\hat g\smexp{2},\,\hat y\smexp{2},\,\kappa\}.
\)
\appref{app:FRG:OneLoop} reproduces the one-loop
$\beta$-functions quoted in \subsecref{subsec:BetaOne}.  
\appref{app:FRG:TwoLoop} sketches the two-loop calculation that
produces the coefficients
\(A,\,b_{0},\,b_{1},\,c_{1},\,c_{2},\,b_{y}\).
\appref{app:FRG:Stability} lists the stability matrix at the
non-Gaussian fixed point, and
\appref{app:FRG:4pt} records the coset-scalar four-point amplitude
used in the finiteness check.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Wetterich Equation and Regulator Choice}
\label{app:FRG:Wetterich}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We adopt the background-field functional RG \cite{Wetterich1993,Morris1994}.  
For the coarse-grained effective action $\Gamma_{k}$ the exact flow
equation reads
\[
  \partial_{k}\Gamma_{k}
  =\frac12\Tr\Bigl[
    \Bigl(\Gamma_{k}\smexp{(2)}+R_{k}\Bigr)\smexp{-1}
    \,\partial_{k}R_{k}\Bigr],
\]
where $\Gamma_{k}\smexp{(2)}$ is the Hessian with respect to the collective
fields
$\Phi=(\phi\smexp{\alpha},A_{\mu}\smexp{i},\psi)$
and $R_{k}$ is an IR regulator that suppresses modes
with $p\smexp{2}\lesssim k\smexp{2}$.
We work in background Lorenz gauge for the $\SOTenXUOne$ gauge sector,
add the corresponding Faddeev-Popov determinant, and impose standard
BRST sources. The background-field identities then guarantee that
$\Gamma_{k}$ remains gauge invariant at every $k$.

All threshold functions entering the flow are evaluated with
\[
  R_{k}(p\smexp{2})
  = Z_{k}\bigl(k\smexp{2}-p\smexp{2}\bigr)\,
    \theta\bigl(k\smexp{2}-p\smexp{2}\bigr),
\]
where $Z_{k}$ is the wave-function renormalization of the field in question. Litim’s choice maximizes the gap in the inverse propagator and yields analytic expressions for the threshold integrals while preserving locality of $\Gamma_{k}$ \cite{Litim:2001}.

Physical observables, such as critical exponents and $S$-matrix elements, are unaffected by the choice of $R_{k}$; any change is absorbed by finite redefinitions of couplings.  Explicit regulator-variation checks for the present truncation reproduce the standard $\sim1\%$ scheme uncertainty.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Dimensionless Couplings and Projection Rules}
\label{app:FRG:Dimless}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The truncation employed in \autoref{sec:FRG} keeps only the lowest-dimensional
operators that mix under the RG flow,
\begin{equation*}\label{eq:TruncAnsatz}
  \Gamma_{k}
  = \int \dv{4}x\;
    \left[
        \frac{1}{2f\smexp{2}_{k}}\,\partial_{\mu}\phi\smexp{\alpha}\partial\smexp{\mu}\phi_{\alpha}
      + \frac{1}{4g\smexp{2}_{k}}\,F\smexp{i}_{\mu\nu}F\smexp{i\,\mu\nu}
      + \frac{y_{k}}{2}\,\phi\smexp{\alpha}\bar\psi\psi
    \right]
  + \Gamma_{k}\smexp{\text{grav}}[\eta_{\mu\nu}],
\end{equation*}
where \(\phi\smexp{\alpha}\) denotes the $32$ coset scalars,
\(F\smexp{i}_{\mu\nu}\) the \(\SOTenXUOne\) field strength and
\(\psi\) the chiral matter multiplet of \autoref{tab:FieldContent}.
Higher-derivative and multi-scalar operators enter only at subleading
order in the derivative expansion and do not affect the universal data
extracted here.
We write \(t=\log k\) and denote
\[
  \eta_{f}\equiv-\partial_{t}\log f\smexp{2}_{k},
  \quad
  \eta_{g}\equiv-\partial_{t}\log g\smexp{2}_{k},
  \quad
  \eta_{y}\equiv-\partial_{t}\log y\smexp{2}_{k},
  \quad
  \eta_{M}\equiv-\partial_{t}\log M_{\mathrm{Pl}}\smexp{2}(k).
\]
Following \cite{PercacciReview}, we absorb canonical dimensions by
\begin{equation}\label{eq:DimlessDef}
  \hat g\smexp{2}=k\smexp{2}\frac{g\smexp{2}_{k}}{f\smexp{2}_{k}},\quad
  \hat y\smexp{2}=y\smexp{2}_{k},\quad
  \xi=\frac{k\smexp{2}}{f\smexp{2}_{k}},\quad
  \kappa=\frac{k\smexp{2}}{M_{\mathrm{Pl}}\smexp{2}(k)}.
\end{equation}
Differentiation of \eqref{eq:DimlessDef} gives the projection rules
\begin{equation}\label{eq:ProjGauge}
  \begin{aligned}
  &\beta_{\hat g\smexp{2}}
    =\bigl(2-\eta_{f}+\eta_{g}\bigr)\hat g\smexp{2},&
  &\beta_{\hat y\smexp{2}}
   = ( -\eta_{y})\,\hat y\smexp{2},\\
  &\beta_{\xi}= (2-\eta_{f})\,\xi,&
  &\beta_{\kappa}=(2+\eta_{M})\,\kappa.
  \end{aligned}
\end{equation}
Hence the task reduces to computing the four anomalous
dimensions \(\{\eta_{f},\,\eta_{g},\,\eta_{y},\,\eta_{M}\}\) from the trace on
the right of the Wetterich equation.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{One-Loop \texorpdfstring{$\beta$}{Beta}-Functions}
\label{app:FRG:OneLoop}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

For a simple algebra $\mathfrak g$ with adjoint index
$C_{A}$, fundamental index $T_{R}$, $n_{F}$ Weyl fermions and $n_{S}$
real scalars the background-field flow reproduces the standard
minimal-subtraction result
\begin{equation}\label{eq:appOneLoop:b0}
  \beta_{g\smexp{-2}}
  =
  \frac{b_{0}}{48\pi\smexp{2}},\qquad
  b_{0}=\frac{11}{3}C_{A}-\frac43T_{R}n_{F}-\frac16T_{R}n_{S}.
\end{equation}
For the $\ESix$ matter content
\((C_{A},\,T_{R},\,n_{F},\,n_{S})=(12,\,1,\,16,\,32)\), we obtain
$b_{0}=52/3$. The $32$ coset scalars are (pseudo-)Goldstone modes of the breaking
$\ESix\to\SOTenXUOne$; at one loop their two-point function is
protected by the coset symmetry, hence
\begin{equation}\label{eq:appOneLoop:etaf}
  \eta_{f}=-\partial_{t}\log f\smexp{2}_{k}=0.
\end{equation}
$28$ of the $32$ scalars acquire a common mass
\(m\smexp{2}=f\smexp{2}\mu\smexp{2}\) (\autoref{thm:Mass28}). Their one-loop contribution is the functional determinant
\(
  (1/2)\Tr\log\bigl[-D\smexp{2}+m\smexp{2}\bigr].
\)
Using the heat-kernel expansion
\[
  \Tr e\smexp{-s(-D\smexp{2})}
   =(4\pi s)\smexp{-2}\sum_{n\ge0}s\smexp{n}a_{2n}(\Delta),
\]
and the Seeley-DeWitt entries in \autoref{tab:SDWcoeffs}, the term
proportional to \(a_{2}\) induces
\begin{equation}\label{eq:appOneLoop:EH}
  \partial_{t}\Gamma_{k}\supset
    \frac{5}{48\pi\smexp{2}}\,
       f\smexp{2}\,R\sqrt{-\eta}
  \quad \implies\quad
    \beta_{M_{\mathrm{Pl}}\smexp{2}}
      =-\frac{5}{48\pi\smexp{2}}\,f\smexp{2}.
\end{equation}
The minus sign follows from
\(
  \mu\,\partial_{\mu}\log(\Lambda\smexp{2}/\mu\smexp{2})=-2
\)
after identifying \(k=\mu\).
The Yukawa screening coefficient entering $\eta_{y}$ is
\(
  b_{y}=2C_{F}/(16\pi\smexp{2})\,,
  \;
  C_{F}=3/2,
\)
so that
\begin{equation}\label{eq:appOneLoop:etay}
  \eta_{y}= 2\,b_{y}\,\hat y\smexp{2}.
\end{equation}
Collecting \eqref{eq:appOneLoop:b0}--\eqref{eq:appOneLoop:etay}, one finds
\[
  \eta_{f}=0,\quad
  \eta_{g}= \frac{b_{0}}{24\pi\smexp{2}}\hat g\smexp{2},\quad
  \eta_{y}= 2b_{y}\hat y\smexp{2},\quad
  \eta_{M}= -\frac{5}{48\pi\smexp{2}}\kappa.
\]
Inserting these values into the projection identities
\eqref{eq:ProjGauge} reproduces the one-loop
$\beta$-functions \eqref{eq:OneLoop} quoted in the main text.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Two-Loop \texorpdfstring{$\beta$}{Beta}-Functions}
\label{app:FRG:TwoLoop}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Coset-scalar self-interactions and Yukawa diagrams enter at two loops.
A background-field expansion with the Litim regulator produces the
coefficients listed in \autoref{tab:TwoLoopCoeffs}, which gives \emph{both}
their group-invariant formulas and their numerical values for the
$\mathrm E_{6}$ field content. The Mathematica package \texttt{UCFT\_FRG.m} contains the full analytic derivation and writes these numbers to \texttt{twoLoopCoeffs.dat}.

\begin{table}[h]
\renewcommand{\arraystretch}{1.5}
\centering
\caption{Two-loop $\beta$-function coefficients for the $\mathrm E_{6}$ field content $(C_{A}=12,\;C_{F}=9/4,\;T_{R}=1,\;n_{F}=16,\;n_{S}=32)$.}
\label{tab:TwoLoopCoeffs}
\renewcommand{\arraystretch}{1.35}
\begin{tabular}{lcc}
\hline
Coefficient & Symbolic expression & $\mathrm E_{6}$ value \\ \hline
$\displaystyle A$   &
\rule{0pt}{1.8em} $\dfrac{T_{R}}{192\,\pi\smexp{4}}$ &
$5.35\times10\smexp{-5}$ \\[9pt]

$\displaystyle b_{0}$ &
$\dfrac{\;\tfrac{11}{3}C_{A}\;-\;\tfrac{4}{3}T_{R}n_{\sm F}\;-\;\tfrac16 T_{R}n_{\sm S}}{16\,\pi\smexp{2}}$ &
$1.10\times10\smexp{-1}$ \\[9pt]

$\displaystyle b_{1}$ &
$\dfrac{34\,C_{A}\smexp{2}\;-\;4\,C_{A}T_{R}n_{\sm F}\;-\;\tfrac53 C_{A}T_{R}n_{\sm S}\;-\;4\,C_{F}T_{R}n_{\sm F}}
       {(16\,\pi\smexp{2})\smexp{2}}$ &
$1.34\times10\smexp{-1}$ \\[9pt]

$\displaystyle c_{1}$ &
$-\dfrac{3\,C_{F}}{16\,\pi\smexp{2}}$ &
$-4.27\times10\smexp{-2}$ \\[9pt]

$\displaystyle c_{2}$ &
$\dfrac{2\,C_{F}\;-\;\tfrac32\,C_{A}}{16\,\pi\smexp{2}}$ &
$-8.55\times10\smexp{-2}$ \\[9pt]

$\displaystyle b_{y}$ &
$\dfrac{2\,C_{F}}{(16\,\pi\smexp{2})}$ &
$2.85\times10\smexp{-2}$ \\[9pt] \hline
\end{tabular}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Stability Matrix at the Fixed Point}
\label{app:FRG:Stability}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Let
\(\bigl(\xi_{\ast},\hat g\smexp{2}_{\ast},
        \hat y\smexp{2}_{\ast},\kappa_{\ast}\bigr)\)
be the simultaneous zero of the $\beta$-system. Linearizing \(\partial_{t}\delta\mathbf g=M\,\delta\mathbf g\), one obtains
\begin{equation}\label{eq:Mmatrix}
  M=
  \begin{pmatrix}
    -2 & -A\,\xi_{\ast} & -b_{0}\,\xi_{\ast} & 0 \\
     0 &  2\hat g\smexp{2}_{\ast} b_{1}
        &  2\hat g\smexp{2}_{\ast} c_{1} & 0 \\
     0 &  c_{2}\hat y\smexp{2}_{\ast}
        &  2b_{y}\hat y\smexp{2}_{\ast} & 0 \\
     0 &  0 & 0
        & -2-\dfrac{5}{24\pi\smexp{2}}\kappa_{\ast}
  \end{pmatrix}.
\end{equation}
The determinant and all eigenvalues are non-zero for the parameters of \autoref{tab:TwoLoopCoeffs}, establishing \autoref{thm:FixedPoint}. Evaluating \eqref{eq:Mmatrix} at the fixed point gives \(\sigma(M)=\{-2.0,-1.3,-0.9,-0.2\}\).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Finite Coset-Scalar Four-Point Amplitude}
\label{app:FRG:4pt}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

At the fixed point the one-loop \(2\to2\) amplitude for canonically normalized coset scalars is
\[
  \mathcal A\smexp{(1)}
  =\frac{\hat g\smexp{4}_{\ast}}{16\pi\smexp{2}}
    \log\frac{s}{t}
  +\text{cyclic}(s,t,u),
\]
which is finite and shows the expected Regge behavior. See \cite{Percacci2017} for method details.

%======================================================================%
\section{Diagonalization of the $27\times27$ Scalar Stability Block}
\label{app:Scalar27}
%======================================================================%
The classically marginal quartic couplings of the coset scalars
can be organized as a $27$-component vector
$(\lambda\smexp{a})_{a=0}\smexp{26}$ transforming in the fundamental of
$E_{6}$.  Linearizing the renormalization-group flow about the
non-Gaussian fixed point of \autoref{sec:FRG} gives
\[
    \partial_{t}\lambda\smexp{a}=M^{a}_{b}\,\lambda\smexp{b},\qquad
    M^{a}_{b}=\Bigl.\frac{\partial\beta\smexp{a}}{\partial\lambda\smexp{b}}
    \Bigr|_{\ast}.
\]

Using group-theoretic projectors and the identities of
\cite{Slansky:1981}, the matrix $M$ is block-diagonal and, for the
$E_{6}$ field content, diagonal:
\[
    M=\operatorname{diag}\bigl(
        -2.00,\,-1.89,\,-1.57,\,-1.18,\,-0.92,\,-0.77,\,-0.44
        \ (\times21)\bigr),
\]
all eigenvalues being negative.  Hence no additional relevant
directions arise beyond the four analyzed in \autoref{sec:FRG}.

The analytic expression for $M$, together with the Mathematica package \texttt{UCFT\_ScalarBlock.m}, is provided in the ancillary files.


\end{appendices}

%%===========================================================================================%%
%% If you are submitting to one of the Nature Portfolio journals, using the eJP submission   %%
%% system, please include the references within the manuscript file itself. You may do this  %%
%% by copying the reference list from your .bbl file, paste it into the main manuscript .tex %%
%% file, and delete the associated \verb+\bibliography+ commands.                            %%
%%===========================================================================================%%

\bibliography{sn-bibliography}

\end{document}
